## 0x96f

```{r, ggsci-iterm-0x96f}
p1 <- p1 + scale_color_iterm("0x96f")
p2 <- p2 + scale_fill_iterm("0x96f")
grid.arrange(p1, p2, ncol = 2)
```

## 12-bit Rainbow

```{r, ggsci-iterm-12-bit-rainbow}
p1 <- p1 + scale_color_iterm("12-bit Rainbow")
p2 <- p2 + scale_fill_iterm("12-bit Rainbow")
grid.arrange(p1, p2, ncol = 2)
```

## 3024 Day

```{r, ggsci-iterm-3024-day}
p1 <- p1 + scale_color_iterm("3024 Day")
p2 <- p2 + scale_fill_iterm("3024 Day")
grid.arrange(p1, p2, ncol = 2)
```

## 3024 Night

```{r, ggsci-iterm-3024-night}
p1 <- p1 + scale_color_iterm("3024 Night")
p2 <- p2 + scale_fill_iterm("3024 Night")
grid.arrange(p1, p2, ncol = 2)
```

## Aardvark Blue

```{r, ggsci-iterm-aardvark-blue}
p1 <- p1 + scale_color_iterm("Aardvark Blue")
p2 <- p2 + scale_fill_iterm("Aardvark Blue")
grid.arrange(p1, p2, ncol = 2)
```

## Abernathy

```{r, ggsci-iterm-abernathy}
p1 <- p1 + scale_color_iterm("Abernathy")
p2 <- p2 + scale_fill_iterm("Abernathy")
grid.arrange(p1, p2, ncol = 2)
```

## Adventure Time

```{r, ggsci-iterm-adventure-time}
p1 <- p1 + scale_color_iterm("Adventure Time")
p2 <- p2 + scale_fill_iterm("Adventure Time")
grid.arrange(p1, p2, ncol = 2)
```

## Adventure

```{r, ggsci-iterm-adventure}
p1 <- p1 + scale_color_iterm("Adventure")
p2 <- p2 + scale_fill_iterm("Adventure")
grid.arrange(p1, p2, ncol = 2)
```

## Adwaita Dark

```{r, ggsci-iterm-adwaita-dark}
p1 <- p1 + scale_color_iterm("Adwaita Dark")
p2 <- p2 + scale_fill_iterm("Adwaita Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Adwaita

```{r, ggsci-iterm-adwaita}
p1 <- p1 + scale_color_iterm("Adwaita")
p2 <- p2 + scale_fill_iterm("Adwaita")
grid.arrange(p1, p2, ncol = 2)
```

## Afterglow

```{r, ggsci-iterm-afterglow}
p1 <- p1 + scale_color_iterm("Afterglow")
p2 <- p2 + scale_fill_iterm("Afterglow")
grid.arrange(p1, p2, ncol = 2)
```

## Alabaster

```{r, ggsci-iterm-alabaster}
p1 <- p1 + scale_color_iterm("Alabaster")
p2 <- p2 + scale_fill_iterm("Alabaster")
grid.arrange(p1, p2, ncol = 2)
```

## Alien Blood

```{r, ggsci-iterm-alien-blood}
p1 <- p1 + scale_color_iterm("Alien Blood")
p2 <- p2 + scale_fill_iterm("Alien Blood")
grid.arrange(p1, p2, ncol = 2)
```

## Andromeda

```{r, ggsci-iterm-andromeda}
p1 <- p1 + scale_color_iterm("Andromeda")
p2 <- p2 + scale_fill_iterm("Andromeda")
grid.arrange(p1, p2, ncol = 2)
```

## Apple Classic

```{r, ggsci-iterm-apple-classic}
p1 <- p1 + scale_color_iterm("Apple Classic")
p2 <- p2 + scale_fill_iterm("Apple Classic")
grid.arrange(p1, p2, ncol = 2)
```

## Apple System Colors Light

```{r, ggsci-iterm-apple-system-colors-light}
p1 <- p1 + scale_color_iterm("Apple System Colors Light")
p2 <- p2 + scale_fill_iterm("Apple System Colors Light")
grid.arrange(p1, p2, ncol = 2)
```

## Apple System Colors

```{r, ggsci-iterm-apple-system-colors}
p1 <- p1 + scale_color_iterm("Apple System Colors")
p2 <- p2 + scale_fill_iterm("Apple System Colors")
grid.arrange(p1, p2, ncol = 2)
```

## Arcoiris

```{r, ggsci-iterm-arcoiris}
p1 <- p1 + scale_color_iterm("Arcoiris")
p2 <- p2 + scale_fill_iterm("Arcoiris")
grid.arrange(p1, p2, ncol = 2)
```

## Ardoise

```{r, ggsci-iterm-ardoise}
p1 <- p1 + scale_color_iterm("Ardoise")
p2 <- p2 + scale_fill_iterm("Ardoise")
grid.arrange(p1, p2, ncol = 2)
```

## Argonaut

```{r, ggsci-iterm-argonaut}
p1 <- p1 + scale_color_iterm("Argonaut")
p2 <- p2 + scale_fill_iterm("Argonaut")
grid.arrange(p1, p2, ncol = 2)
```

## Arthur

```{r, ggsci-iterm-arthur}
p1 <- p1 + scale_color_iterm("Arthur")
p2 <- p2 + scale_fill_iterm("Arthur")
grid.arrange(p1, p2, ncol = 2)
```

## Atelier Sulphurpool

```{r, ggsci-iterm-atelier-sulphurpool}
p1 <- p1 + scale_color_iterm("Atelier Sulphurpool")
p2 <- p2 + scale_fill_iterm("Atelier Sulphurpool")
grid.arrange(p1, p2, ncol = 2)
```

## Atom One Dark

```{r, ggsci-iterm-atom-one-dark}
p1 <- p1 + scale_color_iterm("Atom One Dark")
p2 <- p2 + scale_fill_iterm("Atom One Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Atom One Light

```{r, ggsci-iterm-atom-one-light}
p1 <- p1 + scale_color_iterm("Atom One Light")
p2 <- p2 + scale_fill_iterm("Atom One Light")
grid.arrange(p1, p2, ncol = 2)
```

## Atom

```{r, ggsci-iterm-atom}
p1 <- p1 + scale_color_iterm("Atom")
p2 <- p2 + scale_fill_iterm("Atom")
grid.arrange(p1, p2, ncol = 2)
```

## Aura

```{r, ggsci-iterm-aura}
p1 <- p1 + scale_color_iterm("Aura")
p2 <- p2 + scale_fill_iterm("Aura")
grid.arrange(p1, p2, ncol = 2)
```

## Aurora

```{r, ggsci-iterm-aurora}
p1 <- p1 + scale_color_iterm("Aurora")
p2 <- p2 + scale_fill_iterm("Aurora")
grid.arrange(p1, p2, ncol = 2)
```

## Ayu Light

```{r, ggsci-iterm-ayu-light}
p1 <- p1 + scale_color_iterm("Ayu Light")
p2 <- p2 + scale_fill_iterm("Ayu Light")
grid.arrange(p1, p2, ncol = 2)
```

## Ayu Mirage

```{r, ggsci-iterm-ayu-mirage}
p1 <- p1 + scale_color_iterm("Ayu Mirage")
p2 <- p2 + scale_fill_iterm("Ayu Mirage")
grid.arrange(p1, p2, ncol = 2)
```

## Ayu

```{r, ggsci-iterm-ayu}
p1 <- p1 + scale_color_iterm("Ayu")
p2 <- p2 + scale_fill_iterm("Ayu")
grid.arrange(p1, p2, ncol = 2)
```

## Banana Blueberry

```{r, ggsci-iterm-banana-blueberry}
p1 <- p1 + scale_color_iterm("Banana Blueberry")
p2 <- p2 + scale_fill_iterm("Banana Blueberry")
grid.arrange(p1, p2, ncol = 2)
```

## Batman

```{r, ggsci-iterm-batman}
p1 <- p1 + scale_color_iterm("Batman")
p2 <- p2 + scale_fill_iterm("Batman")
grid.arrange(p1, p2, ncol = 2)
```

## Belafonte Day

```{r, ggsci-iterm-belafonte-day}
p1 <- p1 + scale_color_iterm("Belafonte Day")
p2 <- p2 + scale_fill_iterm("Belafonte Day")
grid.arrange(p1, p2, ncol = 2)
```

## Belafonte Night

```{r, ggsci-iterm-belafonte-night}
p1 <- p1 + scale_color_iterm("Belafonte Night")
p2 <- p2 + scale_fill_iterm("Belafonte Night")
grid.arrange(p1, p2, ncol = 2)
```

## Birds Of Paradise

```{r, ggsci-iterm-birds-of-paradise}
p1 <- p1 + scale_color_iterm("Birds Of Paradise")
p2 <- p2 + scale_fill_iterm("Birds Of Paradise")
grid.arrange(p1, p2, ncol = 2)
```

## Black Metal (Bathory)

```{r, ggsci-iterm-black-metal-bathory}
p1 <- p1 + scale_color_iterm("Black Metal (Bathory)")
p2 <- p2 + scale_fill_iterm("Black Metal (Bathory)")
grid.arrange(p1, p2, ncol = 2)
```

## Black Metal (Burzum)

```{r, ggsci-iterm-black-metal-burzum}
p1 <- p1 + scale_color_iterm("Black Metal (Burzum)")
p2 <- p2 + scale_fill_iterm("Black Metal (Burzum)")
grid.arrange(p1, p2, ncol = 2)
```

## Black Metal (Dark Funeral)

```{r, ggsci-iterm-black-metal-dark-funeral}
p1 <- p1 + scale_color_iterm("Black Metal (Dark Funeral)")
p2 <- p2 + scale_fill_iterm("Black Metal (Dark Funeral)")
grid.arrange(p1, p2, ncol = 2)
```

## Black Metal (Gorgoroth)

```{r, ggsci-iterm-black-metal-gorgoroth}
p1 <- p1 + scale_color_iterm("Black Metal (Gorgoroth)")
p2 <- p2 + scale_fill_iterm("Black Metal (Gorgoroth)")
grid.arrange(p1, p2, ncol = 2)
```

## Black Metal (Immortal)

```{r, ggsci-iterm-black-metal-immortal}
p1 <- p1 + scale_color_iterm("Black Metal (Immortal)")
p2 <- p2 + scale_fill_iterm("Black Metal (Immortal)")
grid.arrange(p1, p2, ncol = 2)
```

## Black Metal (Khold)

```{r, ggsci-iterm-black-metal-khold}
p1 <- p1 + scale_color_iterm("Black Metal (Khold)")
p2 <- p2 + scale_fill_iterm("Black Metal (Khold)")
grid.arrange(p1, p2, ncol = 2)
```

## Black Metal (Marduk)

```{r, ggsci-iterm-black-metal-marduk}
p1 <- p1 + scale_color_iterm("Black Metal (Marduk)")
p2 <- p2 + scale_fill_iterm("Black Metal (Marduk)")
grid.arrange(p1, p2, ncol = 2)
```

## Black Metal (Mayhem)

```{r, ggsci-iterm-black-metal-mayhem}
p1 <- p1 + scale_color_iterm("Black Metal (Mayhem)")
p2 <- p2 + scale_fill_iterm("Black Metal (Mayhem)")
grid.arrange(p1, p2, ncol = 2)
```

## Black Metal (Nile)

```{r, ggsci-iterm-black-metal-nile}
p1 <- p1 + scale_color_iterm("Black Metal (Nile)")
p2 <- p2 + scale_fill_iterm("Black Metal (Nile)")
grid.arrange(p1, p2, ncol = 2)
```

## Black Metal (Venom)

```{r, ggsci-iterm-black-metal-venom}
p1 <- p1 + scale_color_iterm("Black Metal (Venom)")
p2 <- p2 + scale_fill_iterm("Black Metal (Venom)")
grid.arrange(p1, p2, ncol = 2)
```

## Black Metal

```{r, ggsci-iterm-black-metal}
p1 <- p1 + scale_color_iterm("Black Metal")
p2 <- p2 + scale_fill_iterm("Black Metal")
grid.arrange(p1, p2, ncol = 2)
```

## Blazer

```{r, ggsci-iterm-blazer}
p1 <- p1 + scale_color_iterm("Blazer")
p2 <- p2 + scale_fill_iterm("Blazer")
grid.arrange(p1, p2, ncol = 2)
```

## Blue Berry Pie

```{r, ggsci-iterm-blue-berry-pie}
p1 <- p1 + scale_color_iterm("Blue Berry Pie")
p2 <- p2 + scale_fill_iterm("Blue Berry Pie")
grid.arrange(p1, p2, ncol = 2)
```

## Blue Dolphin

```{r, ggsci-iterm-blue-dolphin}
p1 <- p1 + scale_color_iterm("Blue Dolphin")
p2 <- p2 + scale_fill_iterm("Blue Dolphin")
grid.arrange(p1, p2, ncol = 2)
```

## Blue Matrix

```{r, ggsci-iterm-blue-matrix}
p1 <- p1 + scale_color_iterm("Blue Matrix")
p2 <- p2 + scale_fill_iterm("Blue Matrix")
grid.arrange(p1, p2, ncol = 2)
```

## Bluloco Dark

```{r, ggsci-iterm-bluloco-dark}
p1 <- p1 + scale_color_iterm("Bluloco Dark")
p2 <- p2 + scale_fill_iterm("Bluloco Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Bluloco Light

```{r, ggsci-iterm-bluloco-light}
p1 <- p1 + scale_color_iterm("Bluloco Light")
p2 <- p2 + scale_fill_iterm("Bluloco Light")
grid.arrange(p1, p2, ncol = 2)
```

## Borland

```{r, ggsci-iterm-borland}
p1 <- p1 + scale_color_iterm("Borland")
p2 <- p2 + scale_fill_iterm("Borland")
grid.arrange(p1, p2, ncol = 2)
```

## Box

```{r, ggsci-iterm-box}
p1 <- p1 + scale_color_iterm("Box")
p2 <- p2 + scale_fill_iterm("Box")
grid.arrange(p1, p2, ncol = 2)
```

## Breadog

```{r, ggsci-iterm-breadog}
p1 <- p1 + scale_color_iterm("Breadog")
p2 <- p2 + scale_fill_iterm("Breadog")
grid.arrange(p1, p2, ncol = 2)
```

## Breeze

```{r, ggsci-iterm-breeze}
p1 <- p1 + scale_color_iterm("Breeze")
p2 <- p2 + scale_fill_iterm("Breeze")
grid.arrange(p1, p2, ncol = 2)
```

## Bright Lights

```{r, ggsci-iterm-bright-lights}
p1 <- p1 + scale_color_iterm("Bright Lights")
p2 <- p2 + scale_fill_iterm("Bright Lights")
grid.arrange(p1, p2, ncol = 2)
```

## Broadcast

```{r, ggsci-iterm-broadcast}
p1 <- p1 + scale_color_iterm("Broadcast")
p2 <- p2 + scale_fill_iterm("Broadcast")
grid.arrange(p1, p2, ncol = 2)
```

## Brogrammer

```{r, ggsci-iterm-brogrammer}
p1 <- p1 + scale_color_iterm("Brogrammer")
p2 <- p2 + scale_fill_iterm("Brogrammer")
grid.arrange(p1, p2, ncol = 2)
```

## Builtin Dark

```{r, ggsci-iterm-builtin-dark}
p1 <- p1 + scale_color_iterm("Builtin Dark")
p2 <- p2 + scale_fill_iterm("Builtin Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Builtin Light

```{r, ggsci-iterm-builtin-light}
p1 <- p1 + scale_color_iterm("Builtin Light")
p2 <- p2 + scale_fill_iterm("Builtin Light")
grid.arrange(p1, p2, ncol = 2)
```

## Builtin Pastel Dark

```{r, ggsci-iterm-builtin-pastel-dark}
p1 <- p1 + scale_color_iterm("Builtin Pastel Dark")
p2 <- p2 + scale_fill_iterm("Builtin Pastel Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Builtin Solarized Dark

```{r, ggsci-iterm-builtin-solarized-dark}
p1 <- p1 + scale_color_iterm("Builtin Solarized Dark")
p2 <- p2 + scale_fill_iterm("Builtin Solarized Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Builtin Solarized Light

```{r, ggsci-iterm-builtin-solarized-light}
p1 <- p1 + scale_color_iterm("Builtin Solarized Light")
p2 <- p2 + scale_fill_iterm("Builtin Solarized Light")
grid.arrange(p1, p2, ncol = 2)
```

## Builtin Tango Dark

```{r, ggsci-iterm-builtin-tango-dark}
p1 <- p1 + scale_color_iterm("Builtin Tango Dark")
p2 <- p2 + scale_fill_iterm("Builtin Tango Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Builtin Tango Light

```{r, ggsci-iterm-builtin-tango-light}
p1 <- p1 + scale_color_iterm("Builtin Tango Light")
p2 <- p2 + scale_fill_iterm("Builtin Tango Light")
grid.arrange(p1, p2, ncol = 2)
```

## C64

```{r, ggsci-iterm-c64}
p1 <- p1 + scale_color_iterm("C64")
p2 <- p2 + scale_fill_iterm("C64")
grid.arrange(p1, p2, ncol = 2)
```

## Calamity

```{r, ggsci-iterm-calamity}
p1 <- p1 + scale_color_iterm("Calamity")
p2 <- p2 + scale_fill_iterm("Calamity")
grid.arrange(p1, p2, ncol = 2)
```

## Carbonfox

```{r, ggsci-iterm-carbonfox}
p1 <- p1 + scale_color_iterm("Carbonfox")
p2 <- p2 + scale_fill_iterm("Carbonfox")
grid.arrange(p1, p2, ncol = 2)
```

## Catppuccin Frappe

```{r, ggsci-iterm-catppuccin-frappe}
p1 <- p1 + scale_color_iterm("Catppuccin Frappe")
p2 <- p2 + scale_fill_iterm("Catppuccin Frappe")
grid.arrange(p1, p2, ncol = 2)
```

## Catppuccin Latte

```{r, ggsci-iterm-catppuccin-latte}
p1 <- p1 + scale_color_iterm("Catppuccin Latte")
p2 <- p2 + scale_fill_iterm("Catppuccin Latte")
grid.arrange(p1, p2, ncol = 2)
```

## Catppuccin Macchiato

```{r, ggsci-iterm-catppuccin-macchiato}
p1 <- p1 + scale_color_iterm("Catppuccin Macchiato")
p2 <- p2 + scale_fill_iterm("Catppuccin Macchiato")
grid.arrange(p1, p2, ncol = 2)
```

## Catppuccin Mocha

```{r, ggsci-iterm-catppuccin-mocha}
p1 <- p1 + scale_color_iterm("Catppuccin Mocha")
p2 <- p2 + scale_fill_iterm("Catppuccin Mocha")
grid.arrange(p1, p2, ncol = 2)
```

## CGA

```{r, ggsci-iterm-cga}
p1 <- p1 + scale_color_iterm("CGA")
p2 <- p2 + scale_fill_iterm("CGA")
grid.arrange(p1, p2, ncol = 2)
```

## Chalk

```{r, ggsci-iterm-chalk}
p1 <- p1 + scale_color_iterm("Chalk")
p2 <- p2 + scale_fill_iterm("Chalk")
grid.arrange(p1, p2, ncol = 2)
```

## Chalkboard

```{r, ggsci-iterm-chalkboard}
p1 <- p1 + scale_color_iterm("Chalkboard")
p2 <- p2 + scale_fill_iterm("Chalkboard")
grid.arrange(p1, p2, ncol = 2)
```

## Challenger Deep

```{r, ggsci-iterm-challenger-deep}
p1 <- p1 + scale_color_iterm("Challenger Deep")
p2 <- p2 + scale_fill_iterm("Challenger Deep")
grid.arrange(p1, p2, ncol = 2)
```

## Chester

```{r, ggsci-iterm-chester}
p1 <- p1 + scale_color_iterm("Chester")
p2 <- p2 + scale_fill_iterm("Chester")
grid.arrange(p1, p2, ncol = 2)
```

## Ciapre

```{r, ggsci-iterm-ciapre}
p1 <- p1 + scale_color_iterm("Ciapre")
p2 <- p2 + scale_fill_iterm("Ciapre")
grid.arrange(p1, p2, ncol = 2)
```

## Citruszest

```{r, ggsci-iterm-citruszest}
p1 <- p1 + scale_color_iterm("Citruszest")
p2 <- p2 + scale_fill_iterm("Citruszest")
grid.arrange(p1, p2, ncol = 2)
```

## CLRS

```{r, ggsci-iterm-clrs}
p1 <- p1 + scale_color_iterm("CLRS")
p2 <- p2 + scale_fill_iterm("CLRS")
grid.arrange(p1, p2, ncol = 2)
```

## Cobalt Neon

```{r, ggsci-iterm-cobalt-neon}
p1 <- p1 + scale_color_iterm("Cobalt Neon")
p2 <- p2 + scale_fill_iterm("Cobalt Neon")
grid.arrange(p1, p2, ncol = 2)
```

## Cobalt Next Dark

```{r, ggsci-iterm-cobalt-next-dark}
p1 <- p1 + scale_color_iterm("Cobalt Next Dark")
p2 <- p2 + scale_fill_iterm("Cobalt Next Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Cobalt Next Minimal

```{r, ggsci-iterm-cobalt-next-minimal}
p1 <- p1 + scale_color_iterm("Cobalt Next Minimal")
p2 <- p2 + scale_fill_iterm("Cobalt Next Minimal")
grid.arrange(p1, p2, ncol = 2)
```

## Cobalt Next

```{r, ggsci-iterm-cobalt-next}
p1 <- p1 + scale_color_iterm("Cobalt Next")
p2 <- p2 + scale_fill_iterm("Cobalt Next")
grid.arrange(p1, p2, ncol = 2)
```

## Cobalt2

```{r, ggsci-iterm-cobalt2}
p1 <- p1 + scale_color_iterm("Cobalt2")
p2 <- p2 + scale_fill_iterm("Cobalt2")
grid.arrange(p1, p2, ncol = 2)
```

## Coffee Theme

```{r, ggsci-iterm-coffee-theme}
p1 <- p1 + scale_color_iterm("Coffee Theme")
p2 <- p2 + scale_fill_iterm("Coffee Theme")
grid.arrange(p1, p2, ncol = 2)
```

## Crayon Pony Fish

```{r, ggsci-iterm-crayon-pony-fish}
p1 <- p1 + scale_color_iterm("Crayon Pony Fish")
p2 <- p2 + scale_fill_iterm("Crayon Pony Fish")
grid.arrange(p1, p2, ncol = 2)
```

## Cursor Dark

```{r, ggsci-iterm-cursor-dark}
p1 <- p1 + scale_color_iterm("Cursor Dark")
p2 <- p2 + scale_fill_iterm("Cursor Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Cutie Pro

```{r, ggsci-iterm-cutie-pro}
p1 <- p1 + scale_color_iterm("Cutie Pro")
p2 <- p2 + scale_fill_iterm("Cutie Pro")
grid.arrange(p1, p2, ncol = 2)
```

## Cyberdyne

```{r, ggsci-iterm-cyberdyne}
p1 <- p1 + scale_color_iterm("Cyberdyne")
p2 <- p2 + scale_fill_iterm("Cyberdyne")
grid.arrange(p1, p2, ncol = 2)
```

## Cyberpunk Scarlet Protocol

```{r, ggsci-iterm-cyberpunk-scarlet-protocol}
p1 <- p1 + scale_color_iterm("Cyberpunk Scarlet Protocol")
p2 <- p2 + scale_fill_iterm("Cyberpunk Scarlet Protocol")
grid.arrange(p1, p2, ncol = 2)
```

## Cyberpunk

```{r, ggsci-iterm-cyberpunk}
p1 <- p1 + scale_color_iterm("Cyberpunk")
p2 <- p2 + scale_fill_iterm("Cyberpunk")
grid.arrange(p1, p2, ncol = 2)
```

## Dark Modern

```{r, ggsci-iterm-dark-modern}
p1 <- p1 + scale_color_iterm("Dark Modern")
p2 <- p2 + scale_fill_iterm("Dark Modern")
grid.arrange(p1, p2, ncol = 2)
```

## Dark Pastel

```{r, ggsci-iterm-dark-pastel}
p1 <- p1 + scale_color_iterm("Dark Pastel")
p2 <- p2 + scale_fill_iterm("Dark Pastel")
grid.arrange(p1, p2, ncol = 2)
```

## Dark+

```{r, ggsci-iterm-dark-plus}
p1 <- p1 + scale_color_iterm("Dark+")
p2 <- p2 + scale_fill_iterm("Dark+")
grid.arrange(p1, p2, ncol = 2)
```

## Darkermatrix

```{r, ggsci-iterm-darkermatrix}
p1 <- p1 + scale_color_iterm("Darkermatrix")
p2 <- p2 + scale_fill_iterm("Darkermatrix")
grid.arrange(p1, p2, ncol = 2)
```

## Darkmatrix

```{r, ggsci-iterm-darkmatrix}
p1 <- p1 + scale_color_iterm("Darkmatrix")
p2 <- p2 + scale_fill_iterm("Darkmatrix")
grid.arrange(p1, p2, ncol = 2)
```

## Darkside

```{r, ggsci-iterm-darkside}
p1 <- p1 + scale_color_iterm("Darkside")
p2 <- p2 + scale_fill_iterm("Darkside")
grid.arrange(p1, p2, ncol = 2)
```

## Dawnfox

```{r, ggsci-iterm-dawnfox}
p1 <- p1 + scale_color_iterm("Dawnfox")
p2 <- p2 + scale_fill_iterm("Dawnfox")
grid.arrange(p1, p2, ncol = 2)
```

## Dayfox

```{r, ggsci-iterm-dayfox}
p1 <- p1 + scale_color_iterm("Dayfox")
p2 <- p2 + scale_fill_iterm("Dayfox")
grid.arrange(p1, p2, ncol = 2)
```

## Deep

```{r, ggsci-iterm-deep}
p1 <- p1 + scale_color_iterm("Deep")
p2 <- p2 + scale_fill_iterm("Deep")
grid.arrange(p1, p2, ncol = 2)
```

## Desert

```{r, ggsci-iterm-desert}
p1 <- p1 + scale_color_iterm("Desert")
p2 <- p2 + scale_fill_iterm("Desert")
grid.arrange(p1, p2, ncol = 2)
```

## Detuned

```{r, ggsci-iterm-detuned}
p1 <- p1 + scale_color_iterm("Detuned")
p2 <- p2 + scale_fill_iterm("Detuned")
grid.arrange(p1, p2, ncol = 2)
```

## Dimidium

```{r, ggsci-iterm-dimidium}
p1 <- p1 + scale_color_iterm("Dimidium")
p2 <- p2 + scale_fill_iterm("Dimidium")
grid.arrange(p1, p2, ncol = 2)
```

## Dimmed Monokai

```{r, ggsci-iterm-dimmed-monokai}
p1 <- p1 + scale_color_iterm("Dimmed Monokai")
p2 <- p2 + scale_fill_iterm("Dimmed Monokai")
grid.arrange(p1, p2, ncol = 2)
```

## Django Reborn Again

```{r, ggsci-iterm-django-reborn-again}
p1 <- p1 + scale_color_iterm("Django Reborn Again")
p2 <- p2 + scale_fill_iterm("Django Reborn Again")
grid.arrange(p1, p2, ncol = 2)
```

## Django Smooth

```{r, ggsci-iterm-django-smooth}
p1 <- p1 + scale_color_iterm("Django Smooth")
p2 <- p2 + scale_fill_iterm("Django Smooth")
grid.arrange(p1, p2, ncol = 2)
```

## Django

```{r, ggsci-iterm-django}
p1 <- p1 + scale_color_iterm("Django")
p2 <- p2 + scale_fill_iterm("Django")
grid.arrange(p1, p2, ncol = 2)
```

## Doom One

```{r, ggsci-iterm-doom-one}
p1 <- p1 + scale_color_iterm("Doom One")
p2 <- p2 + scale_fill_iterm("Doom One")
grid.arrange(p1, p2, ncol = 2)
```

## Doom Peacock

```{r, ggsci-iterm-doom-peacock}
p1 <- p1 + scale_color_iterm("Doom Peacock")
p2 <- p2 + scale_fill_iterm("Doom Peacock")
grid.arrange(p1, p2, ncol = 2)
```

## Dot Gov

```{r, ggsci-iterm-dot-gov}
p1 <- p1 + scale_color_iterm("Dot Gov")
p2 <- p2 + scale_fill_iterm("Dot Gov")
grid.arrange(p1, p2, ncol = 2)
```

## Dracula

```{r, ggsci-iterm-dracula}
p1 <- p1 + scale_color_iterm("Dracula")
p2 <- p2 + scale_fill_iterm("Dracula")
grid.arrange(p1, p2, ncol = 2)
```

## Dracula+

```{r, ggsci-iterm-dracula-plus}
p1 <- p1 + scale_color_iterm("Dracula+")
p2 <- p2 + scale_fill_iterm("Dracula+")
grid.arrange(p1, p2, ncol = 2)
```

## Duckbones

```{r, ggsci-iterm-duckbones}
p1 <- p1 + scale_color_iterm("Duckbones")
p2 <- p2 + scale_fill_iterm("Duckbones")
grid.arrange(p1, p2, ncol = 2)
```

## Duotone Dark

```{r, ggsci-iterm-duotone-dark}
p1 <- p1 + scale_color_iterm("Duotone Dark")
p2 <- p2 + scale_fill_iterm("Duotone Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Duskfox

```{r, ggsci-iterm-duskfox}
p1 <- p1 + scale_color_iterm("Duskfox")
p2 <- p2 + scale_fill_iterm("Duskfox")
grid.arrange(p1, p2, ncol = 2)
```

## Earthsong

```{r, ggsci-iterm-earthsong}
p1 <- p1 + scale_color_iterm("Earthsong")
p2 <- p2 + scale_fill_iterm("Earthsong")
grid.arrange(p1, p2, ncol = 2)
```

## Electron Highlighter

```{r, ggsci-iterm-electron-highlighter}
p1 <- p1 + scale_color_iterm("Electron Highlighter")
p2 <- p2 + scale_fill_iterm("Electron Highlighter")
grid.arrange(p1, p2, ncol = 2)
```

## Elegant

```{r, ggsci-iterm-elegant}
p1 <- p1 + scale_color_iterm("Elegant")
p2 <- p2 + scale_fill_iterm("Elegant")
grid.arrange(p1, p2, ncol = 2)
```

## Elemental

```{r, ggsci-iterm-elemental}
p1 <- p1 + scale_color_iterm("Elemental")
p2 <- p2 + scale_fill_iterm("Elemental")
grid.arrange(p1, p2, ncol = 2)
```

## Elementary

```{r, ggsci-iterm-elementary}
p1 <- p1 + scale_color_iterm("Elementary")
p2 <- p2 + scale_fill_iterm("Elementary")
grid.arrange(p1, p2, ncol = 2)
```

## Embark

```{r, ggsci-iterm-embark}
p1 <- p1 + scale_color_iterm("Embark")
p2 <- p2 + scale_fill_iterm("Embark")
grid.arrange(p1, p2, ncol = 2)
```

## Embers Dark

```{r, ggsci-iterm-embers-dark}
p1 <- p1 + scale_color_iterm("Embers Dark")
p2 <- p2 + scale_fill_iterm("Embers Dark")
grid.arrange(p1, p2, ncol = 2)
```

## ENCOM

```{r, ggsci-iterm-encom}
p1 <- p1 + scale_color_iterm("ENCOM")
p2 <- p2 + scale_fill_iterm("ENCOM")
grid.arrange(p1, p2, ncol = 2)
```

## Espresso Libre

```{r, ggsci-iterm-espresso-libre}
p1 <- p1 + scale_color_iterm("Espresso Libre")
p2 <- p2 + scale_fill_iterm("Espresso Libre")
grid.arrange(p1, p2, ncol = 2)
```

## Espresso

```{r, ggsci-iterm-espresso}
p1 <- p1 + scale_color_iterm("Espresso")
p2 <- p2 + scale_fill_iterm("Espresso")
grid.arrange(p1, p2, ncol = 2)
```

## Everblush

```{r, ggsci-iterm-everblush}
p1 <- p1 + scale_color_iterm("Everblush")
p2 <- p2 + scale_fill_iterm("Everblush")
grid.arrange(p1, p2, ncol = 2)
```

## Everforest Dark Hard

```{r, ggsci-iterm-everforest-dark-hard}
p1 <- p1 + scale_color_iterm("Everforest Dark Hard")
p2 <- p2 + scale_fill_iterm("Everforest Dark Hard")
grid.arrange(p1, p2, ncol = 2)
```

## Everforest Light Med

```{r, ggsci-iterm-everforest-light-med}
p1 <- p1 + scale_color_iterm("Everforest Light Med")
p2 <- p2 + scale_fill_iterm("Everforest Light Med")
grid.arrange(p1, p2, ncol = 2)
```

## Fahrenheit

```{r, ggsci-iterm-fahrenheit}
p1 <- p1 + scale_color_iterm("Fahrenheit")
p2 <- p2 + scale_fill_iterm("Fahrenheit")
grid.arrange(p1, p2, ncol = 2)
```

## Fairyfloss

```{r, ggsci-iterm-fairyfloss}
p1 <- p1 + scale_color_iterm("Fairyfloss")
p2 <- p2 + scale_fill_iterm("Fairyfloss")
grid.arrange(p1, p2, ncol = 2)
```

## Farmhouse Dark

```{r, ggsci-iterm-farmhouse-dark}
p1 <- p1 + scale_color_iterm("Farmhouse Dark")
p2 <- p2 + scale_fill_iterm("Farmhouse Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Farmhouse Light

```{r, ggsci-iterm-farmhouse-light}
p1 <- p1 + scale_color_iterm("Farmhouse Light")
p2 <- p2 + scale_fill_iterm("Farmhouse Light")
grid.arrange(p1, p2, ncol = 2)
```

## Fideloper

```{r, ggsci-iterm-fideloper}
p1 <- p1 + scale_color_iterm("Fideloper")
p2 <- p2 + scale_fill_iterm("Fideloper")
grid.arrange(p1, p2, ncol = 2)
```

## Firefly Traditional

```{r, ggsci-iterm-firefly-traditional}
p1 <- p1 + scale_color_iterm("Firefly Traditional")
p2 <- p2 + scale_fill_iterm("Firefly Traditional")
grid.arrange(p1, p2, ncol = 2)
```

## Firefox Dev

```{r, ggsci-iterm-firefox-dev}
p1 <- p1 + scale_color_iterm("Firefox Dev")
p2 <- p2 + scale_fill_iterm("Firefox Dev")
grid.arrange(p1, p2, ncol = 2)
```

## Firewatch

```{r, ggsci-iterm-firewatch}
p1 <- p1 + scale_color_iterm("Firewatch")
p2 <- p2 + scale_fill_iterm("Firewatch")
grid.arrange(p1, p2, ncol = 2)
```

## Fish Tank

```{r, ggsci-iterm-fish-tank}
p1 <- p1 + scale_color_iterm("Fish Tank")
p2 <- p2 + scale_fill_iterm("Fish Tank")
grid.arrange(p1, p2, ncol = 2)
```

## Flat

```{r, ggsci-iterm-flat}
p1 <- p1 + scale_color_iterm("Flat")
p2 <- p2 + scale_fill_iterm("Flat")
grid.arrange(p1, p2, ncol = 2)
```

## Flatland

```{r, ggsci-iterm-flatland}
p1 <- p1 + scale_color_iterm("Flatland")
p2 <- p2 + scale_fill_iterm("Flatland")
grid.arrange(p1, p2, ncol = 2)
```

## Flexoki Dark

```{r, ggsci-iterm-flexoki-dark}
p1 <- p1 + scale_color_iterm("Flexoki Dark")
p2 <- p2 + scale_fill_iterm("Flexoki Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Flexoki Light

```{r, ggsci-iterm-flexoki-light}
p1 <- p1 + scale_color_iterm("Flexoki Light")
p2 <- p2 + scale_fill_iterm("Flexoki Light")
grid.arrange(p1, p2, ncol = 2)
```

## Floraverse

```{r, ggsci-iterm-floraverse}
p1 <- p1 + scale_color_iterm("Floraverse")
p2 <- p2 + scale_fill_iterm("Floraverse")
grid.arrange(p1, p2, ncol = 2)
```

## Forest Blue

```{r, ggsci-iterm-forest-blue}
p1 <- p1 + scale_color_iterm("Forest Blue")
p2 <- p2 + scale_fill_iterm("Forest Blue")
grid.arrange(p1, p2, ncol = 2)
```

## Framer

```{r, ggsci-iterm-framer}
p1 <- p1 + scale_color_iterm("Framer")
p2 <- p2 + scale_fill_iterm("Framer")
grid.arrange(p1, p2, ncol = 2)
```

## Front End Delight

```{r, ggsci-iterm-front-end-delight}
p1 <- p1 + scale_color_iterm("Front End Delight")
p2 <- p2 + scale_fill_iterm("Front End Delight")
grid.arrange(p1, p2, ncol = 2)
```

## Fun Forrest

```{r, ggsci-iterm-fun-forrest}
p1 <- p1 + scale_color_iterm("Fun Forrest")
p2 <- p2 + scale_fill_iterm("Fun Forrest")
grid.arrange(p1, p2, ncol = 2)
```

## Galaxy

```{r, ggsci-iterm-galaxy}
p1 <- p1 + scale_color_iterm("Galaxy")
p2 <- p2 + scale_fill_iterm("Galaxy")
grid.arrange(p1, p2, ncol = 2)
```

## Galizur

```{r, ggsci-iterm-galizur}
p1 <- p1 + scale_color_iterm("Galizur")
p2 <- p2 + scale_fill_iterm("Galizur")
grid.arrange(p1, p2, ncol = 2)
```

## Ghostty Default Style Dark

```{r, ggsci-iterm-ghostty-default-style-dark}
p1 <- p1 + scale_color_iterm("Ghostty Default Style Dark")
p2 <- p2 + scale_fill_iterm("Ghostty Default Style Dark")
grid.arrange(p1, p2, ncol = 2)
```

## GitHub Dark Colorblind

```{r, ggsci-iterm-github-dark-colorblind}
p1 <- p1 + scale_color_iterm("GitHub Dark Colorblind")
p2 <- p2 + scale_fill_iterm("GitHub Dark Colorblind")
grid.arrange(p1, p2, ncol = 2)
```

## GitHub Dark Default

```{r, ggsci-iterm-github-dark-default}
p1 <- p1 + scale_color_iterm("GitHub Dark Default")
p2 <- p2 + scale_fill_iterm("GitHub Dark Default")
grid.arrange(p1, p2, ncol = 2)
```

## GitHub Dark Dimmed

```{r, ggsci-iterm-github-dark-dimmed}
p1 <- p1 + scale_color_iterm("GitHub Dark Dimmed")
p2 <- p2 + scale_fill_iterm("GitHub Dark Dimmed")
grid.arrange(p1, p2, ncol = 2)
```

## GitHub Dark High Contrast

```{r, ggsci-iterm-github-dark-high-contrast}
p1 <- p1 + scale_color_iterm("GitHub Dark High Contrast")
p2 <- p2 + scale_fill_iterm("GitHub Dark High Contrast")
grid.arrange(p1, p2, ncol = 2)
```

## GitHub Dark

```{r, ggsci-iterm-github-dark}
p1 <- p1 + scale_color_iterm("GitHub Dark")
p2 <- p2 + scale_fill_iterm("GitHub Dark")
grid.arrange(p1, p2, ncol = 2)
```

## GitHub Light Colorblind

```{r, ggsci-iterm-github-light-colorblind}
p1 <- p1 + scale_color_iterm("GitHub Light Colorblind")
p2 <- p2 + scale_fill_iterm("GitHub Light Colorblind")
grid.arrange(p1, p2, ncol = 2)
```

## GitHub Light Default

```{r, ggsci-iterm-github-light-default}
p1 <- p1 + scale_color_iterm("GitHub Light Default")
p2 <- p2 + scale_fill_iterm("GitHub Light Default")
grid.arrange(p1, p2, ncol = 2)
```

## GitHub Light High Contrast

```{r, ggsci-iterm-github-light-high-contrast}
p1 <- p1 + scale_color_iterm("GitHub Light High Contrast")
p2 <- p2 + scale_fill_iterm("GitHub Light High Contrast")
grid.arrange(p1, p2, ncol = 2)
```

## GitHub

```{r, ggsci-iterm-github}
p1 <- p1 + scale_color_iterm("GitHub")
p2 <- p2 + scale_fill_iterm("GitHub")
grid.arrange(p1, p2, ncol = 2)
```

## GitLab Dark Grey

```{r, ggsci-iterm-gitlab-dark-grey}
p1 <- p1 + scale_color_iterm("GitLab Dark Grey")
p2 <- p2 + scale_fill_iterm("GitLab Dark Grey")
grid.arrange(p1, p2, ncol = 2)
```

## GitLab Dark

```{r, ggsci-iterm-gitlab-dark}
p1 <- p1 + scale_color_iterm("GitLab Dark")
p2 <- p2 + scale_fill_iterm("GitLab Dark")
grid.arrange(p1, p2, ncol = 2)
```

## GitLab Light

```{r, ggsci-iterm-gitlab-light}
p1 <- p1 + scale_color_iterm("GitLab Light")
p2 <- p2 + scale_fill_iterm("GitLab Light")
grid.arrange(p1, p2, ncol = 2)
```

## Glacier

```{r, ggsci-iterm-glacier}
p1 <- p1 + scale_color_iterm("Glacier")
p2 <- p2 + scale_fill_iterm("Glacier")
grid.arrange(p1, p2, ncol = 2)
```

## Grape

```{r, ggsci-iterm-grape}
p1 <- p1 + scale_color_iterm("Grape")
p2 <- p2 + scale_fill_iterm("Grape")
grid.arrange(p1, p2, ncol = 2)
```

## Grass

```{r, ggsci-iterm-grass}
p1 <- p1 + scale_color_iterm("Grass")
p2 <- p2 + scale_fill_iterm("Grass")
grid.arrange(p1, p2, ncol = 2)
```

## Grey Green

```{r, ggsci-iterm-grey-green}
p1 <- p1 + scale_color_iterm("Grey Green")
p2 <- p2 + scale_fill_iterm("Grey Green")
grid.arrange(p1, p2, ncol = 2)
```

## Gruber Darker

```{r, ggsci-iterm-gruber-darker}
p1 <- p1 + scale_color_iterm("Gruber Darker")
p2 <- p2 + scale_fill_iterm("Gruber Darker")
grid.arrange(p1, p2, ncol = 2)
```

## Gruvbox Dark Hard

```{r, ggsci-iterm-gruvbox-dark-hard}
p1 <- p1 + scale_color_iterm("Gruvbox Dark Hard")
p2 <- p2 + scale_fill_iterm("Gruvbox Dark Hard")
grid.arrange(p1, p2, ncol = 2)
```

## Gruvbox Dark

```{r, ggsci-iterm-gruvbox-dark}
p1 <- p1 + scale_color_iterm("Gruvbox Dark")
p2 <- p2 + scale_fill_iterm("Gruvbox Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Gruvbox Light Hard

```{r, ggsci-iterm-gruvbox-light-hard}
p1 <- p1 + scale_color_iterm("Gruvbox Light Hard")
p2 <- p2 + scale_fill_iterm("Gruvbox Light Hard")
grid.arrange(p1, p2, ncol = 2)
```

## Gruvbox Light

```{r, ggsci-iterm-gruvbox-light}
p1 <- p1 + scale_color_iterm("Gruvbox Light")
p2 <- p2 + scale_fill_iterm("Gruvbox Light")
grid.arrange(p1, p2, ncol = 2)
```

## Gruvbox Material Dark

```{r, ggsci-iterm-gruvbox-material-dark}
p1 <- p1 + scale_color_iterm("Gruvbox Material Dark")
p2 <- p2 + scale_fill_iterm("Gruvbox Material Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Gruvbox Material Light

```{r, ggsci-iterm-gruvbox-material-light}
p1 <- p1 + scale_color_iterm("Gruvbox Material Light")
p2 <- p2 + scale_fill_iterm("Gruvbox Material Light")
grid.arrange(p1, p2, ncol = 2)
```

## Gruvbox Material

```{r, ggsci-iterm-gruvbox-material}
p1 <- p1 + scale_color_iterm("Gruvbox Material")
p2 <- p2 + scale_fill_iterm("Gruvbox Material")
grid.arrange(p1, p2, ncol = 2)
```

## Guezwhoz

```{r, ggsci-iterm-guezwhoz}
p1 <- p1 + scale_color_iterm("Guezwhoz")
p2 <- p2 + scale_fill_iterm("Guezwhoz")
grid.arrange(p1, p2, ncol = 2)
```

## Hacktober

```{r, ggsci-iterm-hacktober}
p1 <- p1 + scale_color_iterm("Hacktober")
p2 <- p2 + scale_fill_iterm("Hacktober")
grid.arrange(p1, p2, ncol = 2)
```

## Hardcore

```{r, ggsci-iterm-hardcore}
p1 <- p1 + scale_color_iterm("Hardcore")
p2 <- p2 + scale_fill_iterm("Hardcore")
grid.arrange(p1, p2, ncol = 2)
```

## Harper

```{r, ggsci-iterm-harper}
p1 <- p1 + scale_color_iterm("Harper")
p2 <- p2 + scale_fill_iterm("Harper")
grid.arrange(p1, p2, ncol = 2)
```

## Havn Daggry

```{r, ggsci-iterm-havn-daggry}
p1 <- p1 + scale_color_iterm("Havn Daggry")
p2 <- p2 + scale_fill_iterm("Havn Daggry")
grid.arrange(p1, p2, ncol = 2)
```

## Havn Skumring

```{r, ggsci-iterm-havn-skumring}
p1 <- p1 + scale_color_iterm("Havn Skumring")
p2 <- p2 + scale_fill_iterm("Havn Skumring")
grid.arrange(p1, p2, ncol = 2)
```

## HaX0R Blue

```{r, ggsci-iterm-hax0r-blue}
p1 <- p1 + scale_color_iterm("HaX0R Blue")
p2 <- p2 + scale_fill_iterm("HaX0R Blue")
grid.arrange(p1, p2, ncol = 2)
```

## HaX0R Gr33N

```{r, ggsci-iterm-hax0r-gr33n}
p1 <- p1 + scale_color_iterm("HaX0R Gr33N")
p2 <- p2 + scale_fill_iterm("HaX0R Gr33N")
grid.arrange(p1, p2, ncol = 2)
```

## HaX0R R3D

```{r, ggsci-iterm-hax0r-r3d}
p1 <- p1 + scale_color_iterm("HaX0R R3D")
p2 <- p2 + scale_fill_iterm("HaX0R R3D")
grid.arrange(p1, p2, ncol = 2)
```

## Heeler

```{r, ggsci-iterm-heeler}
p1 <- p1 + scale_color_iterm("Heeler")
p2 <- p2 + scale_fill_iterm("Heeler")
grid.arrange(p1, p2, ncol = 2)
```

## Highway

```{r, ggsci-iterm-highway}
p1 <- p1 + scale_color_iterm("Highway")
p2 <- p2 + scale_fill_iterm("Highway")
grid.arrange(p1, p2, ncol = 2)
```

## Hipster Green

```{r, ggsci-iterm-hipster-green}
p1 <- p1 + scale_color_iterm("Hipster Green")
p2 <- p2 + scale_fill_iterm("Hipster Green")
grid.arrange(p1, p2, ncol = 2)
```

## Hivacruz

```{r, ggsci-iterm-hivacruz}
p1 <- p1 + scale_color_iterm("Hivacruz")
p2 <- p2 + scale_fill_iterm("Hivacruz")
grid.arrange(p1, p2, ncol = 2)
```

## Homebrew

```{r, ggsci-iterm-homebrew}
p1 <- p1 + scale_color_iterm("Homebrew")
p2 <- p2 + scale_fill_iterm("Homebrew")
grid.arrange(p1, p2, ncol = 2)
```

## Hopscotch.256

```{r, ggsci-iterm-hopscotch-256}
p1 <- p1 + scale_color_iterm("Hopscotch.256")
p2 <- p2 + scale_fill_iterm("Hopscotch.256")
grid.arrange(p1, p2, ncol = 2)
```

## Hopscotch

```{r, ggsci-iterm-hopscotch}
p1 <- p1 + scale_color_iterm("Hopscotch")
p2 <- p2 + scale_fill_iterm("Hopscotch")
grid.arrange(p1, p2, ncol = 2)
```

## Horizon Bright

```{r, ggsci-iterm-horizon-bright}
p1 <- p1 + scale_color_iterm("Horizon Bright")
p2 <- p2 + scale_fill_iterm("Horizon Bright")
grid.arrange(p1, p2, ncol = 2)
```

## Horizon

```{r, ggsci-iterm-horizon}
p1 <- p1 + scale_color_iterm("Horizon")
p2 <- p2 + scale_fill_iterm("Horizon")
grid.arrange(p1, p2, ncol = 2)
```

## Hot Dog Stand (Mustard)

```{r, ggsci-iterm-hot-dog-stand-mustard}
p1 <- p1 + scale_color_iterm("Hot Dog Stand (Mustard)")
p2 <- p2 + scale_fill_iterm("Hot Dog Stand (Mustard)")
grid.arrange(p1, p2, ncol = 2)
```

## Hot Dog Stand

```{r, ggsci-iterm-hot-dog-stand}
p1 <- p1 + scale_color_iterm("Hot Dog Stand")
p2 <- p2 + scale_fill_iterm("Hot Dog Stand")
grid.arrange(p1, p2, ncol = 2)
```

## Hurtado

```{r, ggsci-iterm-hurtado}
p1 <- p1 + scale_color_iterm("Hurtado")
p2 <- p2 + scale_fill_iterm("Hurtado")
grid.arrange(p1, p2, ncol = 2)
```

## Hybrid

```{r, ggsci-iterm-hybrid}
p1 <- p1 + scale_color_iterm("Hybrid")
p2 <- p2 + scale_fill_iterm("Hybrid")
grid.arrange(p1, p2, ncol = 2)
```

## IBM 5153 CGA (Black)

```{r, ggsci-iterm-ibm-5153-cga-black}
p1 <- p1 + scale_color_iterm("IBM 5153 CGA (Black)")
p2 <- p2 + scale_fill_iterm("IBM 5153 CGA (Black)")
grid.arrange(p1, p2, ncol = 2)
```

## IBM 5153 CGA

```{r, ggsci-iterm-ibm-5153-cga}
p1 <- p1 + scale_color_iterm("IBM 5153 CGA")
p2 <- p2 + scale_fill_iterm("IBM 5153 CGA")
grid.arrange(p1, p2, ncol = 2)
```

## IC Green PPL

```{r, ggsci-iterm-ic-green-ppl}
p1 <- p1 + scale_color_iterm("IC Green PPL")
p2 <- p2 + scale_fill_iterm("IC Green PPL")
grid.arrange(p1, p2, ncol = 2)
```

## IC Orange PPL

```{r, ggsci-iterm-ic-orange-ppl}
p1 <- p1 + scale_color_iterm("IC Orange PPL")
p2 <- p2 + scale_fill_iterm("IC Orange PPL")
grid.arrange(p1, p2, ncol = 2)
```

## Iceberg Dark

```{r, ggsci-iterm-iceberg-dark}
p1 <- p1 + scale_color_iterm("Iceberg Dark")
p2 <- p2 + scale_fill_iterm("Iceberg Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Iceberg Light

```{r, ggsci-iterm-iceberg-light}
p1 <- p1 + scale_color_iterm("Iceberg Light")
p2 <- p2 + scale_fill_iterm("Iceberg Light")
grid.arrange(p1, p2, ncol = 2)
```

## Idea

```{r, ggsci-iterm-idea}
p1 <- p1 + scale_color_iterm("Idea")
p2 <- p2 + scale_fill_iterm("Idea")
grid.arrange(p1, p2, ncol = 2)
```

## Idle Toes

```{r, ggsci-iterm-idle-toes}
p1 <- p1 + scale_color_iterm("Idle Toes")
p2 <- p2 + scale_fill_iterm("Idle Toes")
grid.arrange(p1, p2, ncol = 2)
```

## IR Black

```{r, ggsci-iterm-ir-black}
p1 <- p1 + scale_color_iterm("IR Black")
p2 <- p2 + scale_fill_iterm("IR Black")
grid.arrange(p1, p2, ncol = 2)
```

## IRIX Console

```{r, ggsci-iterm-irix-console}
p1 <- p1 + scale_color_iterm("IRIX Console")
p2 <- p2 + scale_fill_iterm("IRIX Console")
grid.arrange(p1, p2, ncol = 2)
```

## IRIX Terminal

```{r, ggsci-iterm-irix-terminal}
p1 <- p1 + scale_color_iterm("IRIX Terminal")
p2 <- p2 + scale_fill_iterm("IRIX Terminal")
grid.arrange(p1, p2, ncol = 2)
```

## iTerm2 Dark Background

```{r, ggsci-iterm-iterm2-dark-background}
p1 <- p1 + scale_color_iterm("iTerm2 Dark Background")
p2 <- p2 + scale_fill_iterm("iTerm2 Dark Background")
grid.arrange(p1, p2, ncol = 2)
```

## iTerm2 Default

```{r, ggsci-iterm-iterm2-default}
p1 <- p1 + scale_color_iterm("iTerm2 Default")
p2 <- p2 + scale_fill_iterm("iTerm2 Default")
grid.arrange(p1, p2, ncol = 2)
```

## iTerm2 Light Background

```{r, ggsci-iterm-iterm2-light-background}
p1 <- p1 + scale_color_iterm("iTerm2 Light Background")
p2 <- p2 + scale_fill_iterm("iTerm2 Light Background")
grid.arrange(p1, p2, ncol = 2)
```

## iTerm2 Pastel Dark Background

```{r, ggsci-iterm-iterm2-pastel-dark-background}
p1 <- p1 + scale_color_iterm("iTerm2 Pastel Dark Background")
p2 <- p2 + scale_fill_iterm("iTerm2 Pastel Dark Background")
grid.arrange(p1, p2, ncol = 2)
```

## iTerm2 Smoooooth

```{r, ggsci-iterm-iterm2-smoooooth}
p1 <- p1 + scale_color_iterm("iTerm2 Smoooooth")
p2 <- p2 + scale_fill_iterm("iTerm2 Smoooooth")
grid.arrange(p1, p2, ncol = 2)
```

## iTerm2 Solarized Dark

```{r, ggsci-iterm-iterm2-solarized-dark}
p1 <- p1 + scale_color_iterm("iTerm2 Solarized Dark")
p2 <- p2 + scale_fill_iterm("iTerm2 Solarized Dark")
grid.arrange(p1, p2, ncol = 2)
```

## iTerm2 Solarized Light

```{r, ggsci-iterm-iterm2-solarized-light}
p1 <- p1 + scale_color_iterm("iTerm2 Solarized Light")
p2 <- p2 + scale_fill_iterm("iTerm2 Solarized Light")
grid.arrange(p1, p2, ncol = 2)
```

## iTerm2 Tango Dark

```{r, ggsci-iterm-iterm2-tango-dark}
p1 <- p1 + scale_color_iterm("iTerm2 Tango Dark")
p2 <- p2 + scale_fill_iterm("iTerm2 Tango Dark")
grid.arrange(p1, p2, ncol = 2)
```

## iTerm2 Tango Light

```{r, ggsci-iterm-iterm2-tango-light}
p1 <- p1 + scale_color_iterm("iTerm2 Tango Light")
p2 <- p2 + scale_fill_iterm("iTerm2 Tango Light")
grid.arrange(p1, p2, ncol = 2)
```

## Jackie Brown

```{r, ggsci-iterm-jackie-brown}
p1 <- p1 + scale_color_iterm("Jackie Brown")
p2 <- p2 + scale_fill_iterm("Jackie Brown")
grid.arrange(p1, p2, ncol = 2)
```

## Japanesque

```{r, ggsci-iterm-japanesque}
p1 <- p1 + scale_color_iterm("Japanesque")
p2 <- p2 + scale_fill_iterm("Japanesque")
grid.arrange(p1, p2, ncol = 2)
```

## Jellybeans

```{r, ggsci-iterm-jellybeans}
p1 <- p1 + scale_color_iterm("Jellybeans")
p2 <- p2 + scale_fill_iterm("Jellybeans")
grid.arrange(p1, p2, ncol = 2)
```

## JetBrains Darcula

```{r, ggsci-iterm-jetbrains-darcula}
p1 <- p1 + scale_color_iterm("JetBrains Darcula")
p2 <- p2 + scale_fill_iterm("JetBrains Darcula")
grid.arrange(p1, p2, ncol = 2)
```

## Jubi

```{r, ggsci-iterm-jubi}
p1 <- p1 + scale_color_iterm("Jubi")
p2 <- p2 + scale_fill_iterm("Jubi")
grid.arrange(p1, p2, ncol = 2)
```

## Kanagawa Dragon

```{r, ggsci-iterm-kanagawa-dragon}
p1 <- p1 + scale_color_iterm("Kanagawa Dragon")
p2 <- p2 + scale_fill_iterm("Kanagawa Dragon")
grid.arrange(p1, p2, ncol = 2)
```

## Kanagawa Wave

```{r, ggsci-iterm-kanagawa-wave}
p1 <- p1 + scale_color_iterm("Kanagawa Wave")
p2 <- p2 + scale_fill_iterm("Kanagawa Wave")
grid.arrange(p1, p2, ncol = 2)
```

## Kanagawabones

```{r, ggsci-iterm-kanagawabones}
p1 <- p1 + scale_color_iterm("Kanagawabones")
p2 <- p2 + scale_fill_iterm("Kanagawabones")
grid.arrange(p1, p2, ncol = 2)
```

## Kibble

```{r, ggsci-iterm-kibble}
p1 <- p1 + scale_color_iterm("Kibble")
p2 <- p2 + scale_fill_iterm("Kibble")
grid.arrange(p1, p2, ncol = 2)
```

## Kitty Default

```{r, ggsci-iterm-kitty-default}
p1 <- p1 + scale_color_iterm("Kitty Default")
p2 <- p2 + scale_fill_iterm("Kitty Default")
grid.arrange(p1, p2, ncol = 2)
```

## Kitty Low Contrast

```{r, ggsci-iterm-kitty-low-contrast}
p1 <- p1 + scale_color_iterm("Kitty Low Contrast")
p2 <- p2 + scale_fill_iterm("Kitty Low Contrast")
grid.arrange(p1, p2, ncol = 2)
```

## Kolorit

```{r, ggsci-iterm-kolorit}
p1 <- p1 + scale_color_iterm("Kolorit")
p2 <- p2 + scale_fill_iterm("Kolorit")
grid.arrange(p1, p2, ncol = 2)
```

## Konsolas

```{r, ggsci-iterm-konsolas}
p1 <- p1 + scale_color_iterm("Konsolas")
p2 <- p2 + scale_fill_iterm("Konsolas")
grid.arrange(p1, p2, ncol = 2)
```

## Kurokula

```{r, ggsci-iterm-kurokula}
p1 <- p1 + scale_color_iterm("Kurokula")
p2 <- p2 + scale_fill_iterm("Kurokula")
grid.arrange(p1, p2, ncol = 2)
```

## Lab Fox

```{r, ggsci-iterm-lab-fox}
p1 <- p1 + scale_color_iterm("Lab Fox")
p2 <- p2 + scale_fill_iterm("Lab Fox")
grid.arrange(p1, p2, ncol = 2)
```

## Laser

```{r, ggsci-iterm-laser}
p1 <- p1 + scale_color_iterm("Laser")
p2 <- p2 + scale_fill_iterm("Laser")
grid.arrange(p1, p2, ncol = 2)
```

## Later This Evening

```{r, ggsci-iterm-later-this-evening}
p1 <- p1 + scale_color_iterm("Later This Evening")
p2 <- p2 + scale_fill_iterm("Later This Evening")
grid.arrange(p1, p2, ncol = 2)
```

## Lavandula

```{r, ggsci-iterm-lavandula}
p1 <- p1 + scale_color_iterm("Lavandula")
p2 <- p2 + scale_fill_iterm("Lavandula")
grid.arrange(p1, p2, ncol = 2)
```

## Light Owl

```{r, ggsci-iterm-light-owl}
p1 <- p1 + scale_color_iterm("Light Owl")
p2 <- p2 + scale_fill_iterm("Light Owl")
grid.arrange(p1, p2, ncol = 2)
```

## Liquid Carbon Transparent

```{r, ggsci-iterm-liquid-carbon-transparent}
p1 <- p1 + scale_color_iterm("Liquid Carbon Transparent")
p2 <- p2 + scale_fill_iterm("Liquid Carbon Transparent")
grid.arrange(p1, p2, ncol = 2)
```

## Liquid Carbon

```{r, ggsci-iterm-liquid-carbon}
p1 <- p1 + scale_color_iterm("Liquid Carbon")
p2 <- p2 + scale_fill_iterm("Liquid Carbon")
grid.arrange(p1, p2, ncol = 2)
```

## Lovelace

```{r, ggsci-iterm-lovelace}
p1 <- p1 + scale_color_iterm("Lovelace")
p2 <- p2 + scale_fill_iterm("Lovelace")
grid.arrange(p1, p2, ncol = 2)
```

## Man Page

```{r, ggsci-iterm-man-page}
p1 <- p1 + scale_color_iterm("Man Page")
p2 <- p2 + scale_fill_iterm("Man Page")
grid.arrange(p1, p2, ncol = 2)
```

## Mariana

```{r, ggsci-iterm-mariana}
p1 <- p1 + scale_color_iterm("Mariana")
p2 <- p2 + scale_fill_iterm("Mariana")
grid.arrange(p1, p2, ncol = 2)
```

## Material Dark

```{r, ggsci-iterm-material-dark}
p1 <- p1 + scale_color_iterm("Material Dark")
p2 <- p2 + scale_fill_iterm("Material Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Material Darker

```{r, ggsci-iterm-material-darker}
p1 <- p1 + scale_color_iterm("Material Darker")
p2 <- p2 + scale_fill_iterm("Material Darker")
grid.arrange(p1, p2, ncol = 2)
```

## Material Design Colors

```{r, ggsci-iterm-material-design-colors}
p1 <- p1 + scale_color_iterm("Material Design Colors")
p2 <- p2 + scale_fill_iterm("Material Design Colors")
grid.arrange(p1, p2, ncol = 2)
```

## Material Ocean

```{r, ggsci-iterm-material-ocean}
p1 <- p1 + scale_color_iterm("Material Ocean")
p2 <- p2 + scale_fill_iterm("Material Ocean")
grid.arrange(p1, p2, ncol = 2)
```

## Material

```{r, ggsci-iterm-material}
p1 <- p1 + scale_color_iterm("Material")
p2 <- p2 + scale_fill_iterm("Material")
grid.arrange(p1, p2, ncol = 2)
```

## Mathias

```{r, ggsci-iterm-mathias}
p1 <- p1 + scale_color_iterm("Mathias")
p2 <- p2 + scale_fill_iterm("Mathias")
grid.arrange(p1, p2, ncol = 2)
```

## Matrix

```{r, ggsci-iterm-matrix}
p1 <- p1 + scale_color_iterm("Matrix")
p2 <- p2 + scale_fill_iterm("Matrix")
grid.arrange(p1, p2, ncol = 2)
```

## Matte Black

```{r, ggsci-iterm-matte-black}
p1 <- p1 + scale_color_iterm("Matte Black")
p2 <- p2 + scale_fill_iterm("Matte Black")
grid.arrange(p1, p2, ncol = 2)
```

## Medallion

```{r, ggsci-iterm-medallion}
p1 <- p1 + scale_color_iterm("Medallion")
p2 <- p2 + scale_fill_iterm("Medallion")
grid.arrange(p1, p2, ncol = 2)
```

## Melange Dark

```{r, ggsci-iterm-melange-dark}
p1 <- p1 + scale_color_iterm("Melange Dark")
p2 <- p2 + scale_fill_iterm("Melange Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Melange Light

```{r, ggsci-iterm-melange-light}
p1 <- p1 + scale_color_iterm("Melange Light")
p2 <- p2 + scale_fill_iterm("Melange Light")
grid.arrange(p1, p2, ncol = 2)
```

## Mellifluous

```{r, ggsci-iterm-mellifluous}
p1 <- p1 + scale_color_iterm("Mellifluous")
p2 <- p2 + scale_fill_iterm("Mellifluous")
grid.arrange(p1, p2, ncol = 2)
```

## Mellow

```{r, ggsci-iterm-mellow}
p1 <- p1 + scale_color_iterm("Mellow")
p2 <- p2 + scale_fill_iterm("Mellow")
grid.arrange(p1, p2, ncol = 2)
```

## Miasma

```{r, ggsci-iterm-miasma}
p1 <- p1 + scale_color_iterm("Miasma")
p2 <- p2 + scale_fill_iterm("Miasma")
grid.arrange(p1, p2, ncol = 2)
```

## Midnight In Mojave

```{r, ggsci-iterm-midnight-in-mojave}
p1 <- p1 + scale_color_iterm("Midnight In Mojave")
p2 <- p2 + scale_fill_iterm("Midnight In Mojave")
grid.arrange(p1, p2, ncol = 2)
```

## Mirage

```{r, ggsci-iterm-mirage}
p1 <- p1 + scale_color_iterm("Mirage")
p2 <- p2 + scale_fill_iterm("Mirage")
grid.arrange(p1, p2, ncol = 2)
```

## Misterioso

```{r, ggsci-iterm-misterioso}
p1 <- p1 + scale_color_iterm("Misterioso")
p2 <- p2 + scale_fill_iterm("Misterioso")
grid.arrange(p1, p2, ncol = 2)
```

## Molokai

```{r, ggsci-iterm-molokai}
p1 <- p1 + scale_color_iterm("Molokai")
p2 <- p2 + scale_fill_iterm("Molokai")
grid.arrange(p1, p2, ncol = 2)
```

## Mona Lisa

```{r, ggsci-iterm-mona-lisa}
p1 <- p1 + scale_color_iterm("Mona Lisa")
p2 <- p2 + scale_fill_iterm("Mona Lisa")
grid.arrange(p1, p2, ncol = 2)
```

## Monokai Classic

```{r, ggsci-iterm-monokai-classic}
p1 <- p1 + scale_color_iterm("Monokai Classic")
p2 <- p2 + scale_fill_iterm("Monokai Classic")
grid.arrange(p1, p2, ncol = 2)
```

## Monokai Pro Light Sun

```{r, ggsci-iterm-monokai-pro-light-sun}
p1 <- p1 + scale_color_iterm("Monokai Pro Light Sun")
p2 <- p2 + scale_fill_iterm("Monokai Pro Light Sun")
grid.arrange(p1, p2, ncol = 2)
```

## Monokai Pro Light

```{r, ggsci-iterm-monokai-pro-light}
p1 <- p1 + scale_color_iterm("Monokai Pro Light")
p2 <- p2 + scale_fill_iterm("Monokai Pro Light")
grid.arrange(p1, p2, ncol = 2)
```

## Monokai Pro Machine

```{r, ggsci-iterm-monokai-pro-machine}
p1 <- p1 + scale_color_iterm("Monokai Pro Machine")
p2 <- p2 + scale_fill_iterm("Monokai Pro Machine")
grid.arrange(p1, p2, ncol = 2)
```

## Monokai Pro Octagon

```{r, ggsci-iterm-monokai-pro-octagon}
p1 <- p1 + scale_color_iterm("Monokai Pro Octagon")
p2 <- p2 + scale_fill_iterm("Monokai Pro Octagon")
grid.arrange(p1, p2, ncol = 2)
```

## Monokai Pro Ristretto

```{r, ggsci-iterm-monokai-pro-ristretto}
p1 <- p1 + scale_color_iterm("Monokai Pro Ristretto")
p2 <- p2 + scale_fill_iterm("Monokai Pro Ristretto")
grid.arrange(p1, p2, ncol = 2)
```

## Monokai Pro Spectrum

```{r, ggsci-iterm-monokai-pro-spectrum}
p1 <- p1 + scale_color_iterm("Monokai Pro Spectrum")
p2 <- p2 + scale_fill_iterm("Monokai Pro Spectrum")
grid.arrange(p1, p2, ncol = 2)
```

## Monokai Pro

```{r, ggsci-iterm-monokai-pro}
p1 <- p1 + scale_color_iterm("Monokai Pro")
p2 <- p2 + scale_fill_iterm("Monokai Pro")
grid.arrange(p1, p2, ncol = 2)
```

## Monokai Remastered

```{r, ggsci-iterm-monokai-remastered}
p1 <- p1 + scale_color_iterm("Monokai Remastered")
p2 <- p2 + scale_fill_iterm("Monokai Remastered")
grid.arrange(p1, p2, ncol = 2)
```

## Monokai Soda

```{r, ggsci-iterm-monokai-soda}
p1 <- p1 + scale_color_iterm("Monokai Soda")
p2 <- p2 + scale_fill_iterm("Monokai Soda")
grid.arrange(p1, p2, ncol = 2)
```

## Monokai Vivid

```{r, ggsci-iterm-monokai-vivid}
p1 <- p1 + scale_color_iterm("Monokai Vivid")
p2 <- p2 + scale_fill_iterm("Monokai Vivid")
grid.arrange(p1, p2, ncol = 2)
```

## Moonfly

```{r, ggsci-iterm-moonfly}
p1 <- p1 + scale_color_iterm("Moonfly")
p2 <- p2 + scale_fill_iterm("Moonfly")
grid.arrange(p1, p2, ncol = 2)
```

## N0Tch2K

```{r, ggsci-iterm-n0tch2k}
p1 <- p1 + scale_color_iterm("N0Tch2K")
p2 <- p2 + scale_fill_iterm("N0Tch2K")
grid.arrange(p1, p2, ncol = 2)
```

## Neobones Dark

```{r, ggsci-iterm-neobones-dark}
p1 <- p1 + scale_color_iterm("Neobones Dark")
p2 <- p2 + scale_fill_iterm("Neobones Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Neobones Light

```{r, ggsci-iterm-neobones-light}
p1 <- p1 + scale_color_iterm("Neobones Light")
p2 <- p2 + scale_fill_iterm("Neobones Light")
grid.arrange(p1, p2, ncol = 2)
```

## Neon

```{r, ggsci-iterm-neon}
p1 <- p1 + scale_color_iterm("Neon")
p2 <- p2 + scale_fill_iterm("Neon")
grid.arrange(p1, p2, ncol = 2)
```

## Neopolitan

```{r, ggsci-iterm-neopolitan}
p1 <- p1 + scale_color_iterm("Neopolitan")
p2 <- p2 + scale_fill_iterm("Neopolitan")
grid.arrange(p1, p2, ncol = 2)
```

## Neutron

```{r, ggsci-iterm-neutron}
p1 <- p1 + scale_color_iterm("Neutron")
p2 <- p2 + scale_fill_iterm("Neutron")
grid.arrange(p1, p2, ncol = 2)
```

## Night Lion V1

```{r, ggsci-iterm-night-lion-v1}
p1 <- p1 + scale_color_iterm("Night Lion V1")
p2 <- p2 + scale_fill_iterm("Night Lion V1")
grid.arrange(p1, p2, ncol = 2)
```

## Night Lion V2

```{r, ggsci-iterm-night-lion-v2}
p1 <- p1 + scale_color_iterm("Night Lion V2")
p2 <- p2 + scale_fill_iterm("Night Lion V2")
grid.arrange(p1, p2, ncol = 2)
```

## Night Owl

```{r, ggsci-iterm-night-owl}
p1 <- p1 + scale_color_iterm("Night Owl")
p2 <- p2 + scale_fill_iterm("Night Owl")
grid.arrange(p1, p2, ncol = 2)
```

## Night Owlish Light

```{r, ggsci-iterm-night-owlish-light}
p1 <- p1 + scale_color_iterm("Night Owlish Light")
p2 <- p2 + scale_fill_iterm("Night Owlish Light")
grid.arrange(p1, p2, ncol = 2)
```

## Nightfox

```{r, ggsci-iterm-nightfox}
p1 <- p1 + scale_color_iterm("Nightfox")
p2 <- p2 + scale_fill_iterm("Nightfox")
grid.arrange(p1, p2, ncol = 2)
```

## Niji

```{r, ggsci-iterm-niji}
p1 <- p1 + scale_color_iterm("Niji")
p2 <- p2 + scale_fill_iterm("Niji")
grid.arrange(p1, p2, ncol = 2)
```

## Nocturnal Winter

```{r, ggsci-iterm-nocturnal-winter}
p1 <- p1 + scale_color_iterm("Nocturnal Winter")
p2 <- p2 + scale_fill_iterm("Nocturnal Winter")
grid.arrange(p1, p2, ncol = 2)
```

## Nord Light

```{r, ggsci-iterm-nord-light}
p1 <- p1 + scale_color_iterm("Nord Light")
p2 <- p2 + scale_fill_iterm("Nord Light")
grid.arrange(p1, p2, ncol = 2)
```

## Nord Wave

```{r, ggsci-iterm-nord-wave}
p1 <- p1 + scale_color_iterm("Nord Wave")
p2 <- p2 + scale_fill_iterm("Nord Wave")
grid.arrange(p1, p2, ncol = 2)
```

## Nord

```{r, ggsci-iterm-nord}
p1 <- p1 + scale_color_iterm("Nord")
p2 <- p2 + scale_fill_iterm("Nord")
grid.arrange(p1, p2, ncol = 2)
```

## Nordfox

```{r, ggsci-iterm-nordfox}
p1 <- p1 + scale_color_iterm("Nordfox")
p2 <- p2 + scale_fill_iterm("Nordfox")
grid.arrange(p1, p2, ncol = 2)
```

## Novel

```{r, ggsci-iterm-novel}
p1 <- p1 + scale_color_iterm("Novel")
p2 <- p2 + scale_fill_iterm("Novel")
grid.arrange(p1, p2, ncol = 2)
```

## Nvim Dark

```{r, ggsci-iterm-nvim-dark}
p1 <- p1 + scale_color_iterm("Nvim Dark")
p2 <- p2 + scale_fill_iterm("Nvim Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Nvim Light

```{r, ggsci-iterm-nvim-light}
p1 <- p1 + scale_color_iterm("Nvim Light")
p2 <- p2 + scale_fill_iterm("Nvim Light")
grid.arrange(p1, p2, ncol = 2)
```

## Obsidian

```{r, ggsci-iterm-obsidian}
p1 <- p1 + scale_color_iterm("Obsidian")
p2 <- p2 + scale_fill_iterm("Obsidian")
grid.arrange(p1, p2, ncol = 2)
```

## Ocean

```{r, ggsci-iterm-ocean}
p1 <- p1 + scale_color_iterm("Ocean")
p2 <- p2 + scale_fill_iterm("Ocean")
grid.arrange(p1, p2, ncol = 2)
```

## Oceanic Material

```{r, ggsci-iterm-oceanic-material}
p1 <- p1 + scale_color_iterm("Oceanic Material")
p2 <- p2 + scale_fill_iterm("Oceanic Material")
grid.arrange(p1, p2, ncol = 2)
```

## Oceanic Next

```{r, ggsci-iterm-oceanic-next}
p1 <- p1 + scale_color_iterm("Oceanic Next")
p2 <- p2 + scale_fill_iterm("Oceanic Next")
grid.arrange(p1, p2, ncol = 2)
```

## Ollie

```{r, ggsci-iterm-ollie}
p1 <- p1 + scale_color_iterm("Ollie")
p2 <- p2 + scale_fill_iterm("Ollie")
grid.arrange(p1, p2, ncol = 2)
```

## One Double Dark

```{r, ggsci-iterm-one-double-dark}
p1 <- p1 + scale_color_iterm("One Double Dark")
p2 <- p2 + scale_fill_iterm("One Double Dark")
grid.arrange(p1, p2, ncol = 2)
```

## One Double Light

```{r, ggsci-iterm-one-double-light}
p1 <- p1 + scale_color_iterm("One Double Light")
p2 <- p2 + scale_fill_iterm("One Double Light")
grid.arrange(p1, p2, ncol = 2)
```

## One Half Dark

```{r, ggsci-iterm-one-half-dark}
p1 <- p1 + scale_color_iterm("One Half Dark")
p2 <- p2 + scale_fill_iterm("One Half Dark")
grid.arrange(p1, p2, ncol = 2)
```

## One Half Light

```{r, ggsci-iterm-one-half-light}
p1 <- p1 + scale_color_iterm("One Half Light")
p2 <- p2 + scale_fill_iterm("One Half Light")
grid.arrange(p1, p2, ncol = 2)
```

## Operator Mono Dark

```{r, ggsci-iterm-operator-mono-dark}
p1 <- p1 + scale_color_iterm("Operator Mono Dark")
p2 <- p2 + scale_fill_iterm("Operator Mono Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Overnight Slumber

```{r, ggsci-iterm-overnight-slumber}
p1 <- p1 + scale_color_iterm("Overnight Slumber")
p2 <- p2 + scale_fill_iterm("Overnight Slumber")
grid.arrange(p1, p2, ncol = 2)
```

## Oxocarbon

```{r, ggsci-iterm-oxocarbon}
p1 <- p1 + scale_color_iterm("Oxocarbon")
p2 <- p2 + scale_fill_iterm("Oxocarbon")
grid.arrange(p1, p2, ncol = 2)
```

## Pale Night Hc

```{r, ggsci-iterm-pale-night-hc}
p1 <- p1 + scale_color_iterm("Pale Night Hc")
p2 <- p2 + scale_fill_iterm("Pale Night Hc")
grid.arrange(p1, p2, ncol = 2)
```

## Pandora

```{r, ggsci-iterm-pandora}
p1 <- p1 + scale_color_iterm("Pandora")
p2 <- p2 + scale_fill_iterm("Pandora")
grid.arrange(p1, p2, ncol = 2)
```

## Paraiso Dark

```{r, ggsci-iterm-paraiso-dark}
p1 <- p1 + scale_color_iterm("Paraiso Dark")
p2 <- p2 + scale_fill_iterm("Paraiso Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Paul Millr

```{r, ggsci-iterm-paul-millr}
p1 <- p1 + scale_color_iterm("Paul Millr")
p2 <- p2 + scale_fill_iterm("Paul Millr")
grid.arrange(p1, p2, ncol = 2)
```

## Pencil Dark

```{r, ggsci-iterm-pencil-dark}
p1 <- p1 + scale_color_iterm("Pencil Dark")
p2 <- p2 + scale_fill_iterm("Pencil Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Pencil Light

```{r, ggsci-iterm-pencil-light}
p1 <- p1 + scale_color_iterm("Pencil Light")
p2 <- p2 + scale_fill_iterm("Pencil Light")
grid.arrange(p1, p2, ncol = 2)
```

## Peppermint

```{r, ggsci-iterm-peppermint}
p1 <- p1 + scale_color_iterm("Peppermint")
p2 <- p2 + scale_fill_iterm("Peppermint")
grid.arrange(p1, p2, ncol = 2)
```

## Phala Green Dark

```{r, ggsci-iterm-phala-green-dark}
p1 <- p1 + scale_color_iterm("Phala Green Dark")
p2 <- p2 + scale_fill_iterm("Phala Green Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Piatto Light

```{r, ggsci-iterm-piatto-light}
p1 <- p1 + scale_color_iterm("Piatto Light")
p2 <- p2 + scale_fill_iterm("Piatto Light")
grid.arrange(p1, p2, ncol = 2)
```

## Pnevma

```{r, ggsci-iterm-pnevma}
p1 <- p1 + scale_color_iterm("Pnevma")
p2 <- p2 + scale_fill_iterm("Pnevma")
grid.arrange(p1, p2, ncol = 2)
```

## Poimandres Darker

```{r, ggsci-iterm-poimandres-darker}
p1 <- p1 + scale_color_iterm("Poimandres Darker")
p2 <- p2 + scale_fill_iterm("Poimandres Darker")
grid.arrange(p1, p2, ncol = 2)
```

## Poimandres Storm

```{r, ggsci-iterm-poimandres-storm}
p1 <- p1 + scale_color_iterm("Poimandres Storm")
p2 <- p2 + scale_fill_iterm("Poimandres Storm")
grid.arrange(p1, p2, ncol = 2)
```

## Poimandres White

```{r, ggsci-iterm-poimandres-white}
p1 <- p1 + scale_color_iterm("Poimandres White")
p2 <- p2 + scale_fill_iterm("Poimandres White")
grid.arrange(p1, p2, ncol = 2)
```

## Poimandres

```{r, ggsci-iterm-poimandres}
p1 <- p1 + scale_color_iterm("Poimandres")
p2 <- p2 + scale_fill_iterm("Poimandres")
grid.arrange(p1, p2, ncol = 2)
```

## Popping And Locking

```{r, ggsci-iterm-popping-and-locking}
p1 <- p1 + scale_color_iterm("Popping And Locking")
p2 <- p2 + scale_fill_iterm("Popping And Locking")
grid.arrange(p1, p2, ncol = 2)
```

## Powershell

```{r, ggsci-iterm-powershell}
p1 <- p1 + scale_color_iterm("Powershell")
p2 <- p2 + scale_fill_iterm("Powershell")
grid.arrange(p1, p2, ncol = 2)
```

## Primary

```{r, ggsci-iterm-primary}
p1 <- p1 + scale_color_iterm("Primary")
p2 <- p2 + scale_fill_iterm("Primary")
grid.arrange(p1, p2, ncol = 2)
```

## Pro Light

```{r, ggsci-iterm-pro-light}
p1 <- p1 + scale_color_iterm("Pro Light")
p2 <- p2 + scale_fill_iterm("Pro Light")
grid.arrange(p1, p2, ncol = 2)
```

## Pro

```{r, ggsci-iterm-pro}
p1 <- p1 + scale_color_iterm("Pro")
p2 <- p2 + scale_fill_iterm("Pro")
grid.arrange(p1, p2, ncol = 2)
```

## Purple Rain

```{r, ggsci-iterm-purple-rain}
p1 <- p1 + scale_color_iterm("Purple Rain")
p2 <- p2 + scale_fill_iterm("Purple Rain")
grid.arrange(p1, p2, ncol = 2)
```

## Purplepeter

```{r, ggsci-iterm-purplepeter}
p1 <- p1 + scale_color_iterm("Purplepeter")
p2 <- p2 + scale_fill_iterm("Purplepeter")
grid.arrange(p1, p2, ncol = 2)
```

## Rapture

```{r, ggsci-iterm-rapture}
p1 <- p1 + scale_color_iterm("Rapture")
p2 <- p2 + scale_fill_iterm("Rapture")
grid.arrange(p1, p2, ncol = 2)
```

## Raycast Dark

```{r, ggsci-iterm-raycast-dark}
p1 <- p1 + scale_color_iterm("Raycast Dark")
p2 <- p2 + scale_fill_iterm("Raycast Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Raycast Light

```{r, ggsci-iterm-raycast-light}
p1 <- p1 + scale_color_iterm("Raycast Light")
p2 <- p2 + scale_fill_iterm("Raycast Light")
grid.arrange(p1, p2, ncol = 2)
```

## Rebecca

```{r, ggsci-iterm-rebecca}
p1 <- p1 + scale_color_iterm("Rebecca")
p2 <- p2 + scale_fill_iterm("Rebecca")
grid.arrange(p1, p2, ncol = 2)
```

## Red Alert

```{r, ggsci-iterm-red-alert}
p1 <- p1 + scale_color_iterm("Red Alert")
p2 <- p2 + scale_fill_iterm("Red Alert")
grid.arrange(p1, p2, ncol = 2)
```

## Red Planet

```{r, ggsci-iterm-red-planet}
p1 <- p1 + scale_color_iterm("Red Planet")
p2 <- p2 + scale_fill_iterm("Red Planet")
grid.arrange(p1, p2, ncol = 2)
```

## Red Sands

```{r, ggsci-iterm-red-sands}
p1 <- p1 + scale_color_iterm("Red Sands")
p2 <- p2 + scale_fill_iterm("Red Sands")
grid.arrange(p1, p2, ncol = 2)
```

## Relaxed

```{r, ggsci-iterm-relaxed}
p1 <- p1 + scale_color_iterm("Relaxed")
p2 <- p2 + scale_fill_iterm("Relaxed")
grid.arrange(p1, p2, ncol = 2)
```

## Retro Legends

```{r, ggsci-iterm-retro-legends}
p1 <- p1 + scale_color_iterm("Retro Legends")
p2 <- p2 + scale_fill_iterm("Retro Legends")
grid.arrange(p1, p2, ncol = 2)
```

## Retro

```{r, ggsci-iterm-retro}
p1 <- p1 + scale_color_iterm("Retro")
p2 <- p2 + scale_fill_iterm("Retro")
grid.arrange(p1, p2, ncol = 2)
```

## Rippedcasts

```{r, ggsci-iterm-rippedcasts}
p1 <- p1 + scale_color_iterm("Rippedcasts")
p2 <- p2 + scale_fill_iterm("Rippedcasts")
grid.arrange(p1, p2, ncol = 2)
```

## Rose Pine Dawn

```{r, ggsci-iterm-rose-pine-dawn}
p1 <- p1 + scale_color_iterm("Rose Pine Dawn")
p2 <- p2 + scale_fill_iterm("Rose Pine Dawn")
grid.arrange(p1, p2, ncol = 2)
```

## Rose Pine Moon

```{r, ggsci-iterm-rose-pine-moon}
p1 <- p1 + scale_color_iterm("Rose Pine Moon")
p2 <- p2 + scale_fill_iterm("Rose Pine Moon")
grid.arrange(p1, p2, ncol = 2)
```

## Rose Pine

```{r, ggsci-iterm-rose-pine}
p1 <- p1 + scale_color_iterm("Rose Pine")
p2 <- p2 + scale_fill_iterm("Rose Pine")
grid.arrange(p1, p2, ncol = 2)
```

## Rouge 2

```{r, ggsci-iterm-rouge-2}
p1 <- p1 + scale_color_iterm("Rouge 2")
p2 <- p2 + scale_fill_iterm("Rouge 2")
grid.arrange(p1, p2, ncol = 2)
```

## Royal

```{r, ggsci-iterm-royal}
p1 <- p1 + scale_color_iterm("Royal")
p2 <- p2 + scale_fill_iterm("Royal")
grid.arrange(p1, p2, ncol = 2)
```

## Ryuuko

```{r, ggsci-iterm-ryuuko}
p1 <- p1 + scale_color_iterm("Ryuuko")
p2 <- p2 + scale_fill_iterm("Ryuuko")
grid.arrange(p1, p2, ncol = 2)
```

## Sakura

```{r, ggsci-iterm-sakura}
p1 <- p1 + scale_color_iterm("Sakura")
p2 <- p2 + scale_fill_iterm("Sakura")
grid.arrange(p1, p2, ncol = 2)
```

## Scarlet Protocol

```{r, ggsci-iterm-scarlet-protocol}
p1 <- p1 + scale_color_iterm("Scarlet Protocol")
p2 <- p2 + scale_fill_iterm("Scarlet Protocol")
grid.arrange(p1, p2, ncol = 2)
```

## Sea Shells

```{r, ggsci-iterm-sea-shells}
p1 <- p1 + scale_color_iterm("Sea Shells")
p2 <- p2 + scale_fill_iterm("Sea Shells")
grid.arrange(p1, p2, ncol = 2)
```

## Seafoam Pastel

```{r, ggsci-iterm-seafoam-pastel}
p1 <- p1 + scale_color_iterm("Seafoam Pastel")
p2 <- p2 + scale_fill_iterm("Seafoam Pastel")
grid.arrange(p1, p2, ncol = 2)
```

## Selenized Black

```{r, ggsci-iterm-selenized-black}
p1 <- p1 + scale_color_iterm("Selenized Black")
p2 <- p2 + scale_fill_iterm("Selenized Black")
grid.arrange(p1, p2, ncol = 2)
```

## Selenized Dark

```{r, ggsci-iterm-selenized-dark}
p1 <- p1 + scale_color_iterm("Selenized Dark")
p2 <- p2 + scale_fill_iterm("Selenized Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Selenized Light

```{r, ggsci-iterm-selenized-light}
p1 <- p1 + scale_color_iterm("Selenized Light")
p2 <- p2 + scale_fill_iterm("Selenized Light")
grid.arrange(p1, p2, ncol = 2)
```

## Seoulbones Dark

```{r, ggsci-iterm-seoulbones-dark}
p1 <- p1 + scale_color_iterm("Seoulbones Dark")
p2 <- p2 + scale_fill_iterm("Seoulbones Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Seoulbones Light

```{r, ggsci-iterm-seoulbones-light}
p1 <- p1 + scale_color_iterm("Seoulbones Light")
p2 <- p2 + scale_fill_iterm("Seoulbones Light")
grid.arrange(p1, p2, ncol = 2)
```

## Seti

```{r, ggsci-iterm-seti}
p1 <- p1 + scale_color_iterm("Seti")
p2 <- p2 + scale_fill_iterm("Seti")
grid.arrange(p1, p2, ncol = 2)
```

## Shades Of Purple

```{r, ggsci-iterm-shades-of-purple}
p1 <- p1 + scale_color_iterm("Shades Of Purple")
p2 <- p2 + scale_fill_iterm("Shades Of Purple")
grid.arrange(p1, p2, ncol = 2)
```

## Shaman

```{r, ggsci-iterm-shaman}
p1 <- p1 + scale_color_iterm("Shaman")
p2 <- p2 + scale_fill_iterm("Shaman")
grid.arrange(p1, p2, ncol = 2)
```

## Slate

```{r, ggsci-iterm-slate}
p1 <- p1 + scale_color_iterm("Slate")
p2 <- p2 + scale_fill_iterm("Slate")
grid.arrange(p1, p2, ncol = 2)
```

## Sleepy Hollow

```{r, ggsci-iterm-sleepy-hollow}
p1 <- p1 + scale_color_iterm("Sleepy Hollow")
p2 <- p2 + scale_fill_iterm("Sleepy Hollow")
grid.arrange(p1, p2, ncol = 2)
```

## Smyck

```{r, ggsci-iterm-smyck}
p1 <- p1 + scale_color_iterm("Smyck")
p2 <- p2 + scale_fill_iterm("Smyck")
grid.arrange(p1, p2, ncol = 2)
```

## Snazzy Soft

```{r, ggsci-iterm-snazzy-soft}
p1 <- p1 + scale_color_iterm("Snazzy Soft")
p2 <- p2 + scale_fill_iterm("Snazzy Soft")
grid.arrange(p1, p2, ncol = 2)
```

## Snazzy

```{r, ggsci-iterm-snazzy}
p1 <- p1 + scale_color_iterm("Snazzy")
p2 <- p2 + scale_fill_iterm("Snazzy")
grid.arrange(p1, p2, ncol = 2)
```

## Soft Server

```{r, ggsci-iterm-soft-server}
p1 <- p1 + scale_color_iterm("Soft Server")
p2 <- p2 + scale_fill_iterm("Soft Server")
grid.arrange(p1, p2, ncol = 2)
```

## Solarized Darcula

```{r, ggsci-iterm-solarized-darcula}
p1 <- p1 + scale_color_iterm("Solarized Darcula")
p2 <- p2 + scale_fill_iterm("Solarized Darcula")
grid.arrange(p1, p2, ncol = 2)
```

## Solarized Dark Higher Contrast

```{r, ggsci-iterm-solarized-dark-higher-contrast}
p1 <- p1 + scale_color_iterm("Solarized Dark Higher Contrast")
p2 <- p2 + scale_fill_iterm("Solarized Dark Higher Contrast")
grid.arrange(p1, p2, ncol = 2)
```

## Solarized Dark Patched

```{r, ggsci-iterm-solarized-dark-patched}
p1 <- p1 + scale_color_iterm("Solarized Dark Patched")
p2 <- p2 + scale_fill_iterm("Solarized Dark Patched")
grid.arrange(p1, p2, ncol = 2)
```

## Solarized Osaka Night

```{r, ggsci-iterm-solarized-osaka-night}
p1 <- p1 + scale_color_iterm("Solarized Osaka Night")
p2 <- p2 + scale_fill_iterm("Solarized Osaka Night")
grid.arrange(p1, p2, ncol = 2)
```

## Sonokai

```{r, ggsci-iterm-sonokai}
p1 <- p1 + scale_color_iterm("Sonokai")
p2 <- p2 + scale_fill_iterm("Sonokai")
grid.arrange(p1, p2, ncol = 2)
```

## Spacedust

```{r, ggsci-iterm-spacedust}
p1 <- p1 + scale_color_iterm("Spacedust")
p2 <- p2 + scale_fill_iterm("Spacedust")
grid.arrange(p1, p2, ncol = 2)
```

## Spacegray Bright

```{r, ggsci-iterm-spacegray-bright}
p1 <- p1 + scale_color_iterm("Spacegray Bright")
p2 <- p2 + scale_fill_iterm("Spacegray Bright")
grid.arrange(p1, p2, ncol = 2)
```

## Spacegray Eighties Dull

```{r, ggsci-iterm-spacegray-eighties-dull}
p1 <- p1 + scale_color_iterm("Spacegray Eighties Dull")
p2 <- p2 + scale_fill_iterm("Spacegray Eighties Dull")
grid.arrange(p1, p2, ncol = 2)
```

## Spacegray Eighties

```{r, ggsci-iterm-spacegray-eighties}
p1 <- p1 + scale_color_iterm("Spacegray Eighties")
p2 <- p2 + scale_fill_iterm("Spacegray Eighties")
grid.arrange(p1, p2, ncol = 2)
```

## Spacegray

```{r, ggsci-iterm-spacegray}
p1 <- p1 + scale_color_iterm("Spacegray")
p2 <- p2 + scale_fill_iterm("Spacegray")
grid.arrange(p1, p2, ncol = 2)
```

## Spiderman

```{r, ggsci-iterm-spiderman}
p1 <- p1 + scale_color_iterm("Spiderman")
p2 <- p2 + scale_fill_iterm("Spiderman")
grid.arrange(p1, p2, ncol = 2)
```

## Spring

```{r, ggsci-iterm-spring}
p1 <- p1 + scale_color_iterm("Spring")
p2 <- p2 + scale_fill_iterm("Spring")
grid.arrange(p1, p2, ncol = 2)
```

## Square

```{r, ggsci-iterm-square}
p1 <- p1 + scale_color_iterm("Square")
p2 <- p2 + scale_fill_iterm("Square")
grid.arrange(p1, p2, ncol = 2)
```

## Squirrelsong Dark

```{r, ggsci-iterm-squirrelsong-dark}
p1 <- p1 + scale_color_iterm("Squirrelsong Dark")
p2 <- p2 + scale_fill_iterm("Squirrelsong Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Srcery

```{r, ggsci-iterm-srcery}
p1 <- p1 + scale_color_iterm("Srcery")
p2 <- p2 + scale_fill_iterm("Srcery")
grid.arrange(p1, p2, ncol = 2)
```

## Starlight

```{r, ggsci-iterm-starlight}
p1 <- p1 + scale_color_iterm("Starlight")
p2 <- p2 + scale_fill_iterm("Starlight")
grid.arrange(p1, p2, ncol = 2)
```

## Sublette

```{r, ggsci-iterm-sublette}
p1 <- p1 + scale_color_iterm("Sublette")
p2 <- p2 + scale_fill_iterm("Sublette")
grid.arrange(p1, p2, ncol = 2)
```

## Subliminal

```{r, ggsci-iterm-subliminal}
p1 <- p1 + scale_color_iterm("Subliminal")
p2 <- p2 + scale_fill_iterm("Subliminal")
grid.arrange(p1, p2, ncol = 2)
```

## Sugarplum

```{r, ggsci-iterm-sugarplum}
p1 <- p1 + scale_color_iterm("Sugarplum")
p2 <- p2 + scale_fill_iterm("Sugarplum")
grid.arrange(p1, p2, ncol = 2)
```

## Sundried

```{r, ggsci-iterm-sundried}
p1 <- p1 + scale_color_iterm("Sundried")
p2 <- p2 + scale_fill_iterm("Sundried")
grid.arrange(p1, p2, ncol = 2)
```

## Symfonic

```{r, ggsci-iterm-symfonic}
p1 <- p1 + scale_color_iterm("Symfonic")
p2 <- p2 + scale_fill_iterm("Symfonic")
grid.arrange(p1, p2, ncol = 2)
```

## Synthwave Alpha

```{r, ggsci-iterm-synthwave-alpha}
p1 <- p1 + scale_color_iterm("Synthwave Alpha")
p2 <- p2 + scale_fill_iterm("Synthwave Alpha")
grid.arrange(p1, p2, ncol = 2)
```

## Synthwave Everything

```{r, ggsci-iterm-synthwave-everything}
p1 <- p1 + scale_color_iterm("Synthwave Everything")
p2 <- p2 + scale_fill_iterm("Synthwave Everything")
grid.arrange(p1, p2, ncol = 2)
```

## Synthwave

```{r, ggsci-iterm-synthwave}
p1 <- p1 + scale_color_iterm("Synthwave")
p2 <- p2 + scale_fill_iterm("Synthwave")
grid.arrange(p1, p2, ncol = 2)
```

## Tango Adapted

```{r, ggsci-iterm-tango-adapted}
p1 <- p1 + scale_color_iterm("Tango Adapted")
p2 <- p2 + scale_fill_iterm("Tango Adapted")
grid.arrange(p1, p2, ncol = 2)
```

## Tango Half Adapted

```{r, ggsci-iterm-tango-half-adapted}
p1 <- p1 + scale_color_iterm("Tango Half Adapted")
p2 <- p2 + scale_fill_iterm("Tango Half Adapted")
grid.arrange(p1, p2, ncol = 2)
```

## Tearout

```{r, ggsci-iterm-tearout}
p1 <- p1 + scale_color_iterm("Tearout")
p2 <- p2 + scale_fill_iterm("Tearout")
grid.arrange(p1, p2, ncol = 2)
```

## Teerb

```{r, ggsci-iterm-teerb}
p1 <- p1 + scale_color_iterm("Teerb")
p2 <- p2 + scale_fill_iterm("Teerb")
grid.arrange(p1, p2, ncol = 2)
```

## Terafox

```{r, ggsci-iterm-terafox}
p1 <- p1 + scale_color_iterm("Terafox")
p2 <- p2 + scale_fill_iterm("Terafox")
grid.arrange(p1, p2, ncol = 2)
```

## Terminal Basic Dark

```{r, ggsci-iterm-terminal-basic-dark}
p1 <- p1 + scale_color_iterm("Terminal Basic Dark")
p2 <- p2 + scale_fill_iterm("Terminal Basic Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Terminal Basic

```{r, ggsci-iterm-terminal-basic}
p1 <- p1 + scale_color_iterm("Terminal Basic")
p2 <- p2 + scale_fill_iterm("Terminal Basic")
grid.arrange(p1, p2, ncol = 2)
```

## Thayer Bright

```{r, ggsci-iterm-thayer-bright}
p1 <- p1 + scale_color_iterm("Thayer Bright")
p2 <- p2 + scale_fill_iterm("Thayer Bright")
grid.arrange(p1, p2, ncol = 2)
```

## The Hulk

```{r, ggsci-iterm-the-hulk}
p1 <- p1 + scale_color_iterm("The Hulk")
p2 <- p2 + scale_fill_iterm("The Hulk")
grid.arrange(p1, p2, ncol = 2)
```

## Tinacious Design Dark

```{r, ggsci-iterm-tinacious-design-dark}
p1 <- p1 + scale_color_iterm("Tinacious Design Dark")
p2 <- p2 + scale_fill_iterm("Tinacious Design Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Tinacious Design Light

```{r, ggsci-iterm-tinacious-design-light}
p1 <- p1 + scale_color_iterm("Tinacious Design Light")
p2 <- p2 + scale_fill_iterm("Tinacious Design Light")
grid.arrange(p1, p2, ncol = 2)
```

## TokyoNight Day

```{r, ggsci-iterm-tokyonight-day}
p1 <- p1 + scale_color_iterm("TokyoNight Day")
p2 <- p2 + scale_fill_iterm("TokyoNight Day")
grid.arrange(p1, p2, ncol = 2)
```

## TokyoNight Moon

```{r, ggsci-iterm-tokyonight-moon}
p1 <- p1 + scale_color_iterm("TokyoNight Moon")
p2 <- p2 + scale_fill_iterm("TokyoNight Moon")
grid.arrange(p1, p2, ncol = 2)
```

## TokyoNight Night

```{r, ggsci-iterm-tokyonight-night}
p1 <- p1 + scale_color_iterm("TokyoNight Night")
p2 <- p2 + scale_fill_iterm("TokyoNight Night")
grid.arrange(p1, p2, ncol = 2)
```

## TokyoNight Storm

```{r, ggsci-iterm-tokyonight-storm}
p1 <- p1 + scale_color_iterm("TokyoNight Storm")
p2 <- p2 + scale_fill_iterm("TokyoNight Storm")
grid.arrange(p1, p2, ncol = 2)
```

## TokyoNight

```{r, ggsci-iterm-tokyonight}
p1 <- p1 + scale_color_iterm("TokyoNight")
p2 <- p2 + scale_fill_iterm("TokyoNight")
grid.arrange(p1, p2, ncol = 2)
```

## Tomorrow Night Blue

```{r, ggsci-iterm-tomorrow-night-blue}
p1 <- p1 + scale_color_iterm("Tomorrow Night Blue")
p2 <- p2 + scale_fill_iterm("Tomorrow Night Blue")
grid.arrange(p1, p2, ncol = 2)
```

## Tomorrow Night Bright

```{r, ggsci-iterm-tomorrow-night-bright}
p1 <- p1 + scale_color_iterm("Tomorrow Night Bright")
p2 <- p2 + scale_fill_iterm("Tomorrow Night Bright")
grid.arrange(p1, p2, ncol = 2)
```

## Tomorrow Night Burns

```{r, ggsci-iterm-tomorrow-night-burns}
p1 <- p1 + scale_color_iterm("Tomorrow Night Burns")
p2 <- p2 + scale_fill_iterm("Tomorrow Night Burns")
grid.arrange(p1, p2, ncol = 2)
```

## Tomorrow Night Eighties

```{r, ggsci-iterm-tomorrow-night-eighties}
p1 <- p1 + scale_color_iterm("Tomorrow Night Eighties")
p2 <- p2 + scale_fill_iterm("Tomorrow Night Eighties")
grid.arrange(p1, p2, ncol = 2)
```

## Tomorrow Night

```{r, ggsci-iterm-tomorrow-night}
p1 <- p1 + scale_color_iterm("Tomorrow Night")
p2 <- p2 + scale_fill_iterm("Tomorrow Night")
grid.arrange(p1, p2, ncol = 2)
```

## Tomorrow

```{r, ggsci-iterm-tomorrow}
p1 <- p1 + scale_color_iterm("Tomorrow")
p2 <- p2 + scale_fill_iterm("Tomorrow")
grid.arrange(p1, p2, ncol = 2)
```

## Toy Chest

```{r, ggsci-iterm-toy-chest}
p1 <- p1 + scale_color_iterm("Toy Chest")
p2 <- p2 + scale_fill_iterm("Toy Chest")
grid.arrange(p1, p2, ncol = 2)
```

## Treehouse

```{r, ggsci-iterm-treehouse}
p1 <- p1 + scale_color_iterm("Treehouse")
p2 <- p2 + scale_fill_iterm("Treehouse")
grid.arrange(p1, p2, ncol = 2)
```

## Twilight

```{r, ggsci-iterm-twilight}
p1 <- p1 + scale_color_iterm("Twilight")
p2 <- p2 + scale_fill_iterm("Twilight")
grid.arrange(p1, p2, ncol = 2)
```

## Ubuntu

```{r, ggsci-iterm-ubuntu}
p1 <- p1 + scale_color_iterm("Ubuntu")
p2 <- p2 + scale_fill_iterm("Ubuntu")
grid.arrange(p1, p2, ncol = 2)
```

## Ultra Dark

```{r, ggsci-iterm-ultra-dark}
p1 <- p1 + scale_color_iterm("Ultra Dark")
p2 <- p2 + scale_fill_iterm("Ultra Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Ultra Violent

```{r, ggsci-iterm-ultra-violent}
p1 <- p1 + scale_color_iterm("Ultra Violent")
p2 <- p2 + scale_fill_iterm("Ultra Violent")
grid.arrange(p1, p2, ncol = 2)
```

## Under The Sea

```{r, ggsci-iterm-under-the-sea}
p1 <- p1 + scale_color_iterm("Under The Sea")
p2 <- p2 + scale_fill_iterm("Under The Sea")
grid.arrange(p1, p2, ncol = 2)
```

## Unikitty

```{r, ggsci-iterm-unikitty}
p1 <- p1 + scale_color_iterm("Unikitty")
p2 <- p2 + scale_fill_iterm("Unikitty")
grid.arrange(p1, p2, ncol = 2)
```

## Urple

```{r, ggsci-iterm-urple}
p1 <- p1 + scale_color_iterm("Urple")
p2 <- p2 + scale_fill_iterm("Urple")
grid.arrange(p1, p2, ncol = 2)
```

## Vague

```{r, ggsci-iterm-vague}
p1 <- p1 + scale_color_iterm("Vague")
p2 <- p2 + scale_fill_iterm("Vague")
grid.arrange(p1, p2, ncol = 2)
```

## Vaughn

```{r, ggsci-iterm-vaughn}
p1 <- p1 + scale_color_iterm("Vaughn")
p2 <- p2 + scale_fill_iterm("Vaughn")
grid.arrange(p1, p2, ncol = 2)
```

## Vercel

```{r, ggsci-iterm-vercel}
p1 <- p1 + scale_color_iterm("Vercel")
p2 <- p2 + scale_fill_iterm("Vercel")
grid.arrange(p1, p2, ncol = 2)
```

## Vesper

```{r, ggsci-iterm-vesper}
p1 <- p1 + scale_color_iterm("Vesper")
p2 <- p2 + scale_fill_iterm("Vesper")
grid.arrange(p1, p2, ncol = 2)
```

## Vibrant Ink

```{r, ggsci-iterm-vibrant-ink}
p1 <- p1 + scale_color_iterm("Vibrant Ink")
p2 <- p2 + scale_fill_iterm("Vibrant Ink")
grid.arrange(p1, p2, ncol = 2)
```

## Vimbones

```{r, ggsci-iterm-vimbones}
p1 <- p1 + scale_color_iterm("Vimbones")
p2 <- p2 + scale_fill_iterm("Vimbones")
grid.arrange(p1, p2, ncol = 2)
```

## Violet Dark

```{r, ggsci-iterm-violet-dark}
p1 <- p1 + scale_color_iterm("Violet Dark")
p2 <- p2 + scale_fill_iterm("Violet Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Violet Light

```{r, ggsci-iterm-violet-light}
p1 <- p1 + scale_color_iterm("Violet Light")
p2 <- p2 + scale_fill_iterm("Violet Light")
grid.arrange(p1, p2, ncol = 2)
```

## Violite

```{r, ggsci-iterm-violite}
p1 <- p1 + scale_color_iterm("Violite")
p2 <- p2 + scale_fill_iterm("Violite")
grid.arrange(p1, p2, ncol = 2)
```

## Warm Neon

```{r, ggsci-iterm-warm-neon}
p1 <- p1 + scale_color_iterm("Warm Neon")
p2 <- p2 + scale_fill_iterm("Warm Neon")
grid.arrange(p1, p2, ncol = 2)
```

## Wez

```{r, ggsci-iterm-wez}
p1 <- p1 + scale_color_iterm("Wez")
p2 <- p2 + scale_fill_iterm("Wez")
grid.arrange(p1, p2, ncol = 2)
```

## Whimsy

```{r, ggsci-iterm-whimsy}
p1 <- p1 + scale_color_iterm("Whimsy")
p2 <- p2 + scale_fill_iterm("Whimsy")
grid.arrange(p1, p2, ncol = 2)
```

## Wild Cherry

```{r, ggsci-iterm-wild-cherry}
p1 <- p1 + scale_color_iterm("Wild Cherry")
p2 <- p2 + scale_fill_iterm("Wild Cherry")
grid.arrange(p1, p2, ncol = 2)
```

## Wilmersdorf

```{r, ggsci-iterm-wilmersdorf}
p1 <- p1 + scale_color_iterm("Wilmersdorf")
p2 <- p2 + scale_fill_iterm("Wilmersdorf")
grid.arrange(p1, p2, ncol = 2)
```

## Wombat

```{r, ggsci-iterm-wombat}
p1 <- p1 + scale_color_iterm("Wombat")
p2 <- p2 + scale_fill_iterm("Wombat")
grid.arrange(p1, p2, ncol = 2)
```

## Wryan

```{r, ggsci-iterm-wryan}
p1 <- p1 + scale_color_iterm("Wryan")
p2 <- p2 + scale_fill_iterm("Wryan")
grid.arrange(p1, p2, ncol = 2)
```

## Xcode Dark hc

```{r, ggsci-iterm-xcode-dark-hc}
p1 <- p1 + scale_color_iterm("Xcode Dark hc")
p2 <- p2 + scale_fill_iterm("Xcode Dark hc")
grid.arrange(p1, p2, ncol = 2)
```

## Xcode Dark

```{r, ggsci-iterm-xcode-dark}
p1 <- p1 + scale_color_iterm("Xcode Dark")
p2 <- p2 + scale_fill_iterm("Xcode Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Xcode Light hc

```{r, ggsci-iterm-xcode-light-hc}
p1 <- p1 + scale_color_iterm("Xcode Light hc")
p2 <- p2 + scale_fill_iterm("Xcode Light hc")
grid.arrange(p1, p2, ncol = 2)
```

## Xcode Light

```{r, ggsci-iterm-xcode-light}
p1 <- p1 + scale_color_iterm("Xcode Light")
p2 <- p2 + scale_fill_iterm("Xcode Light")
grid.arrange(p1, p2, ncol = 2)
```

## Xcode WWDC

```{r, ggsci-iterm-xcode-wwdc}
p1 <- p1 + scale_color_iterm("Xcode WWDC")
p2 <- p2 + scale_fill_iterm("Xcode WWDC")
grid.arrange(p1, p2, ncol = 2)
```

## Zenbones Dark

```{r, ggsci-iterm-zenbones-dark}
p1 <- p1 + scale_color_iterm("Zenbones Dark")
p2 <- p2 + scale_fill_iterm("Zenbones Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Zenbones Light

```{r, ggsci-iterm-zenbones-light}
p1 <- p1 + scale_color_iterm("Zenbones Light")
p2 <- p2 + scale_fill_iterm("Zenbones Light")
grid.arrange(p1, p2, ncol = 2)
```

## Zenbones

```{r, ggsci-iterm-zenbones}
p1 <- p1 + scale_color_iterm("Zenbones")
p2 <- p2 + scale_fill_iterm("Zenbones")
grid.arrange(p1, p2, ncol = 2)
```

## Zenburn

```{r, ggsci-iterm-zenburn}
p1 <- p1 + scale_color_iterm("Zenburn")
p2 <- p2 + scale_fill_iterm("Zenburn")
grid.arrange(p1, p2, ncol = 2)
```

## Zenburned

```{r, ggsci-iterm-zenburned}
p1 <- p1 + scale_color_iterm("Zenburned")
p2 <- p2 + scale_fill_iterm("Zenburned")
grid.arrange(p1, p2, ncol = 2)
```

## Zenwritten Dark

```{r, ggsci-iterm-zenwritten-dark}
p1 <- p1 + scale_color_iterm("Zenwritten Dark")
p2 <- p2 + scale_fill_iterm("Zenwritten Dark")
grid.arrange(p1, p2, ncol = 2)
```

## Zenwritten Light

```{r, ggsci-iterm-zenwritten-light}
p1 <- p1 + scale_color_iterm("Zenwritten Light")
p2 <- p2 + scale_fill_iterm("Zenwritten Light")
grid.arrange(p1, p2, ncol = 2)
```

